---
title: "BLC CLT and Word Properties"
date: "2026-04-01"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
options(scipen = 999) #removes scietific notation
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lme4)
library(broom.mixed) #for RMarkdown tables
library(knitr) #for RMarkdown tables
library(afex)
library(gtsummary)
library(flextable)
library(officer)
library(simr)
```

```{r data, include=FALSE}
data_pl <- read_csv("data_clt_wp_pl_anon.csv")
data_no <- read_csv("data_clt_wp_no_anon.csv")
```

## Data prepation

Step 1. Removing outliers from RTs
Outliers are defined as RTs that are both higher 
than mean RT + 3SD of a given child in a given task 
AND mean RT + 3SD of a given task

Database filtered for complete datapoints (frequency), 
correct responses and measured RTs higher than 1000 ms 
(lower are typically measurement errors)

Step 2. Scaling

```{r outliers-rts-pl, include=FALSE}
data_pl_filtered <- data_pl %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_pl_filtered$reaction_time) 
#there are 11236 measured reaction times for correct responses and complete cases, 
#RTs>=1000 ms

mean_RT_PL <- data_pl_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_PL <- mean_RT_PL %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_pl_with_outliers <- data_pl_filtered %>%
  left_join(mean_RT_PL, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_pl_meanRTs <- data_pl_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), 
            .groups = "drop")

data_pl_with_outliers <- data_pl_with_outliers %>%
  left_join(data_pl_meanRTs , by = "task") %>%
  mutate(outlier_overall = (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_PL <- data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_PL)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
#We also scale the frequency, imageability and AoA
#This database will be used for the analyses of the reaction times
data_pl_out_outliers <- data_pl_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")
```

```{r scale-pl, include=FALSE}
#data without RT outliers for RT analyses
#frequency is on a log scale but frquency cds needs to be transformed
data_pl_out_outliers <- data_pl_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds),
                                     center = T, scale = T),
    frequency_scaled = scale(FrequencyLemmaLog, 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time))

data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#data with RT outliers for accuracy analyses
data_pl <- data_pl %>%
  mutate(
     frequency_cds_scaled = scale(log(frequency_cds+1), 
                                      center = T, scale = T),
     frequency_scaled = scale(FrequencyLemmaLog, 
                              center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

summary(data_pl)
data_pl$group <-relevel(factor(data_pl$group), ref="monoPL")
```

```{r outliers-rts-no, include=FALSE}
data_no_filtered <- data_no %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_no_filtered$reaction_time)  
#there are 9850 measured reaction times for correct responses and complete cases, RTs>=1000 ms
  
mean_RT_NOR <- data_no_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_NOR <- mean_RT_NOR %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_no_with_outliers <- data_no_filtered %>%
  left_join(mean_RT_NOR, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = 
           (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_no_meanRTs <- data_no_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), .groups = "drop")

data_no_with_outliers <- data_no_with_outliers %>%
  left_join(data_no_meanRTs , by = "task") %>%
  mutate(outlier_overall = 
           (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_no <- data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_no)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
data_no_out_outliers <- data_no_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
```

NO CDS frequency is scaled on the formula:
ln(x+1) (bc there are same frequencies = 0)

```{r scale-no, include=FALSE}
data_no_out_outliers <- data_no_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE),
    logRT=log(reaction_time))

data_no_out_outliers$group <-relevel(factor(data_no_out_outliers$group), ref="monoNO")

#and for accuracy analyses we only need scaling the variables, no outliers
data_no <- data_no %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency + 1), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, center = TRUE, 
                                scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

data_no$group <-relevel(factor(data_no$group), ref="monoNO")
```

## Correlations between word properties

```{r include = FALSE}
df_num <- data_pl %>%
  distinct(word, frequency_cds_scaled, frequency_scaled, Imageability, AoA) %>%
  select(-word)

cor_mat_spearman <- cor(df_num,
                        method = "spearman",
                        use = "complete.obs")

library(Hmisc)
cor_res <- rcorr(as.matrix(df_num), type = "spearman")
# correlation matrix
cor_res$r
# p-values
cor_res$P
```

```{r echo = FALSE}
library(corrplot)
corrplot(cor_res$r,
         p.mat = cor_res$P,
         sig.level = 0.05,
         method = "circle",
         type = "upper",
         tl.col = "black",
         diag = FALSE,
         insig = "blank")
```

Lack of correlation between frequency is suprising...

```{r echo = FALSE}
df_num %>% 
  ggplot(aes(x = frequency_scaled, y = frequency_cds_scaled)) +
  geom_point(color = "lightpink", alpha = .8) +
  theme_classic() +
  labs(x = "SUBTLEX",
       y = "CDS")
```

## Accuracy Models

We run all models together (divided only into accuracy and RTs):

1) Bind Polish and Norwegian data (with outliers)
2) Run and view accuracy models
3) Summarise the results

### Scale age and bind data

```{r acc-data-scale-age, include = FALSE}
#scale and center age
data_pl$Age_scaled <- scale(data_pl$Age, center = T, scale = T)
data_no$Age_scaled <- scale(data_no$Age, center = T, scale = T)
```

```{r bind data, include = FALSE}
bind_rows(data_pl, data_no) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full
```

### Prepare models

```{r models-accuracy-all, echo = FALSE}
formula_glmer <- accuracy_strict ~ 
  Age_scaled +
  group * (AoA_scaled + 
             imageability_scaled + 
             frequency_cds_scaled) +
  imageability_scaled * frequency_cds_scaled +
  (1 + AoA_scaled + 
     imageability_scaled + 
     frequency_cds_scaled | child_id) +
  (1 | word)

ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_acc    = list(language = "POLISH",    task = "P"),
  polish_c_acc    = list(language = "POLISH",    task = "C"),
  norwegian_p_acc = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_acc = list(language = "NORWEGIAN", task = "C")
)

models_acc <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full, language == cond$language & task == cond$task)
  glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)
})

# models
summary(models_acc)
```

Check convergence:
No warnings.

```{r convergence-acc-checks, echo = FALSE}
lapply(models_acc, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r, echo = FALSE}
summary(models_acc$polish_c_acc)
```

### Polish Production

```{r, echo = FALSE}
summary(models_acc$polish_p_acc)
```

### Norwegian Comprehension

```{r, echo = FALSE}
summary(models_acc$norwegian_c_acc)
```

### Norwegian Production

```{r, echo = FALSE}
summary(models_acc$norwegian_p_acc)
```

### Extract table

```{r tables-accuracy-models, eval = FALSE}
# Build a merged table
merged_table <- tbl_merge(
  tbls = lapply(models_acc, function(m) tbl_regression(m, exponentiate = TRUE)),
  tab_spanner = names(models_acc)   # uses list names as column headers
)

# Export
doc <- read_docx() %>%
  body_add_flextable(as_flex_table(merged_table))

print(doc, target = "glmer_summary.docx")
```

##  RTs models

### Scale age and bind data

```{r rt-data-scale-age}
#scale and center age
data_pl_out_outliers$Age_scaled <- scale(data_pl_out_outliers$Age, center = T, scale = T)
data_no_out_outliers$Age_scaled <- scale(data_no_out_outliers$Age, center = T, scale = T)
```

```{r bind-rt-data}
bind_rows(data_pl_out_outliers, data_no_out_outliers) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full_out_outliers
```

### Prepare all models

First more complex with random slopes:

```{r models-rts-all}
formula_lmer <- logRT ~ Age_scaled + 
  group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        imageability_scaled * frequency_cds_scaled +
                        (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + 
  (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt)
```

Most models did not converge: _boundary (singular) fit_

```{r convergence-rt-checks}
lapply(models_rt, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

We proceed with simpler models (no random slopes)

```{r models-rts-all-simple}
formula_lmer_simpler <- logRT ~ Age_scaled + 
  group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
  imageability_scaled * frequency_cds_scaled +
  (1 | child_id) + (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt_simpler <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer_simpler, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt_simpler)
```

```{r convergence-rt-checks-2}
lapply(models_rt_simpler, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_rt_simpler$polish_c_rt)
```

### Polish Production

```{r}
summary(models_rt_simpler$polish_p_rt)
```

### Norwegian Comprehension

```{r}
summary(models_rt_simpler$norwegian_c_rt)
```

### Norwegian Production

```{r}
summary(models_rt_simpler$norwegian_p_rt)
```

### Export Tables

```{r tables-rts-models, eval = FALSE}
# Build a merged table
merged_table_rt <- tbl_merge(
  tbls = lapply(models_rt_simpler, function(m) tbl_regression(m, exponentiate = TRUE)),
  tab_spanner = names(models_rt_simpler)   # uses list names as column headers
)

# Export
doc_rt <- read_docx() |>
  body_add_flextable(as_flex_table(merged_table_rt))

print(doc_rt, target = "lmer_summary.docx")
```
  

# Exposure and Accuracy

```{r select-bi}
data_full %>% filter(group == "bi") -> data_bi_full
```

```{r explore-exposure}
data_bi_full %>% 
  distinct(child_id, no_input_sum_percentage) %>%
  ggplot(aes(x = no_input_sum_percentage)) +
  geom_density()
  
data_bi_full %>% 
  distinct(child_id, pl_input_sum_percentage) %>%
  ggplot(aes(x = pl_input_sum_percentage)) +
  geom_density()
```

```{r exposure-accuracy-models}
conditions <- list(
  polish_p_exposure    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)

models_acc_exposure <- lapply(conditions, function(cond) {
  df_sub <- subset(data_bi_full, language == cond$language & task == cond$task)
  
  formula_glmer <- as.formula(paste0(
    "accuracy_strict ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + (1 | word)"
  ))
  
  glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)
})
```

```{r convergence-acc-exposure-checks}
lapply(models_acc_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_acc_exposure$polish_c_exposure)
```
 
### Polish Production

```{r}
summary(models_acc_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r}
summary(models_acc_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r}
summary(models_acc_exposure$norwegian_p_exposure)
``` 

# Exposure and RTs

```{r select-bi-no-outliers}
data_full_out_outliers %>% filter(group == "bi") -> data_bi_full_rt
```

```{r exposure-rt-models}
conditions <- list(
  polish_p_exposure_rt    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure_rt    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure_rt = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure_rt = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)

models_rt_exposure <- lapply(conditions, function(cond) {
  df_sub <- subset(data_bi_full_rt, language == cond$language & task == cond$task)
  
  formula_lmer <- as.formula(paste0(
    "logRT ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 | child_id) + (1 | word)"
  ))
  
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})
```

```{r convergence-rt-exposure-checks}
lapply(models_rt_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_rt_exposure$polish_c_exposure)
```
 
### Polish Production

```{r}
summary(models_rt_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r}
summary(models_rt_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r}
summary(models_rt_exposure$norwegian_p_exposure)
``` 
  
### Power analysis

EFs from the previous literature
group*AoA_scaled: ns (Łuniewska et al., 2022)
group*imageability_scaled: ns (Łuniewska et al., 2022)
group*frequency_cds_scaled: exp(-.20) = 0.82 (Łuniewska et al., 2022)
Age_scaled*AoA_scaled: ?
Age_scaled*imageability_scaled: ns in Coffey
Age_scaled*frequency_cds_scaled: 1.06 (Coffey et al., 2024); exp(0.82) = 1.22
imageability_scaled*frequency_cds_scaled: 1.36 (Coffey et al., 2024)

We focused on the effects established in the literature.

EFs from Łuniewska et al. (2022); the most relavant in terms of the task and 
children's age range; other effects from Coffey et al. (2024) 
data for imageability specifically and for interaction between imageability and frequency.

Focus on production - data in Coffey available for producion, 
more variability in production data.

```{r effects-previous-lit}
"effect_group_frequency" = -0.20 #Łuniewska et al. (2022)
"effect_Age_imageability" = 1.06 #Coffey et al. (2024)
"effect_imageability_frequency" = 0.38 #Coffey et al. (2024)
```

_"Power analyses were conducted using the structure of the fitted model (random effects, data structure) as the basis for simulation, with fixed effects replaced by estimates from prior literature. In the absence of pilot data, random effect variance components were taken from the present sample, which introduces uncertainty into the power estimates. Results should therefore be interpreted as approximations conditional on the observed variance structure rather than precise a priori power calculations."_ (from Claude)

### Group interaction

```{r}
model_power <- glmer(accuracy_strict ~ 
                       group * (AoA_scaled + 
                                  imageability_scaled + 
                                  frequency_cds_scaled) + 
                       (1 | child_id) +
                       (1 | word),
                            data = data_full %>% filter(language == "POLISH" & task == "P"),
                            family = binomial,
                            control = glmerControl(optimizer = "bobyqa", 
                                                   optCtrl = list(maxfun = 2e5)))
summary(model_power)
```

Power analysis frequency

```{r pa-frequency}
# Use the literature-derived effect, with sign matching your hypothesis
fixef(model_power)["groupbi:frequency_cds_scaled"] <- effect_group_frequency

#power analysis
pwr_analysis_group_frequency <- powerSim(model_power, 
         test = fixed("groupbi:frequency_cds_scaled", method = "z"),
         nsim = 500)
pwr_analysis_group_frequency
beepr::beep(sound = 1)

#extend sample size
model_power2 <- extend(model_power, along="child_id", n=150)
pwr_analysis_group_frequency2 <- powerSim(model_power2, 
         test = fixed("groupbi:frequency_cds_scaled", method = "z"),
         nsim = 500)
 pwr_analysis_group_frequency2
```
