---
title: "BLC CLT and Word Properties"
date: "2026-04-01"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lme4)
library(broom.mixed) #for RMarkdown tables
library(knitr) #for RMarkdown tables
library(afex)
```

```{r data, include=FALSE}
data_pl <- read_csv("data_clt_wp_pl_anon.csv")
data_no <- read_csv("data_clt_wp_no_anon.csv")
```

## Data prepation

Step 1. Removing outliers from RTs
Outliers are defined as RTs that are both higher 
than mean RT + 3SD of a given child in a given task 
AND mean RT + 3SD of a given task

Database filtered for complete datapoints (frequency), 
correct responses and measured RTs higher than 1000 ms 
(lower are typically measurement errors)

Step 2. Scaling

```{r outliers-rts-pl, include=FALSE}
data_pl_filtered <- data_pl %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_pl_filtered$reaction_time) 
#there are 11236 measured reaction times for correct responses and complete cases, RTs>=1000 ms

mean_RT_PL <- data_pl_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_PL <- mean_RT_PL %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_pl_with_outliers <- data_pl_filtered %>%
  left_join(mean_RT_PL, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_pl_meanRTs <- data_pl_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), 
            .groups = "drop")

data_pl_with_outliers <- data_pl_with_outliers %>%
  left_join(data_pl_meanRTs , by = "task") %>%
  mutate(outlier_overall = (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_PL <- data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_PL)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
#We also scale the frequency, imageability and AoA
#This database will be used for the analyses of the reaction times
data_pl_out_outliers <- data_pl_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")
```

```{r scale-pl, include=FALSE}
#data without RT outliers for RT analyses
#frequency is on a log scale but frquency cds needs to be transformed
data_pl_out_outliers <- data_pl_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds),
                                     center = T, scale = T),
    frequency_scaled = scale(FrequencyLemmaLog, 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time))

data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#data with RT outliers for accuracy analyses
data_pl <- data_pl %>%
  mutate(
     frequency_cds_scaled = scale(log(frequency_cds+1), 
                                      center = T, scale = T),
     frequency_scaled = scale(FrequencyLemmaLog, 
                              center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

summary(data_pl)
data_pl$group <-relevel(factor(data_pl$group), ref="monoPL")
```

```{r outliers-rts-no, include=FALSE}
data_no_filtered <- data_no %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_no_filtered$reaction_time)  
#there are 9850 measured reaction times for correct responses and complete cases, RTs>=1000 ms
  
mean_RT_NOR <- data_no_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_NOR <- mean_RT_NOR %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_no_with_outliers <- data_no_filtered %>%
  left_join(mean_RT_NOR, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = 
           (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_no_meanRTs <- data_no_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), .groups = "drop")

data_no_with_outliers <- data_no_with_outliers %>%
  left_join(data_no_meanRTs , by = "task") %>%
  mutate(outlier_overall = 
           (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_no <- data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_no)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
data_no_out_outliers <- data_no_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
```

NO CDS frequency is scaled on the formula:
ln(x+1) (bc there are same frequencies = 0)

```{r scale-no, include=FALSE}
data_no_out_outliers <- data_no_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE),
    logRT=log(reaction_time))

data_no_out_outliers$group <-relevel(factor(data_no_out_outliers$group), ref="monoNO")

#and for accuracy analyses we only need scaling the variables, no outliers
data_no <- data_no %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency + 1), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, center = TRUE, 
                                scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

data_no$group <-relevel(factor(data_no$group), ref="monoNO")
```

## Correlations between word properties

```{r include = FALSE}
df_num <- data_pl %>%
  distinct(word, frequency_cds_scaled, frequency_scaled, Imageability, AoA) %>%
  select(-word)

cor_mat_spearman <- cor(df_num,
                        method = "spearman",
                        use = "complete.obs")

library(Hmisc)
cor_res <- rcorr(as.matrix(df_num), type = "spearman")
# correlation matrix
cor_res$r
# p-values
cor_res$P
```

```{r echo = FALSE}
library(corrplot)
corrplot(cor_res$r,
         p.mat = cor_res$P,
         sig.level = 0.05,
         method = "circle",
         type = "upper",
         tl.col = "black",
         diag = FALSE,
         insig = "blank")
```

Lack of correlation between frequency is suprising...

```{r echo =FALSE}
df_num %>% 
  ggplot(aes(x = frequency_scaled, y = frequency_cds_scaled)) +
  geom_point(color = "lightpink", alpha = .8) +
  theme_classic() +
  labs(x = "SUBTLEX",
       y = "CDS")
```

##  Mixed Models

### Polish

#### Comprehension Accuracy

We begin our analyses with more complex models that include 
by-child random slopes for the lexical predictors, 
and then proceed to simpler models to evaluate 
whether the added complexity improves model fit and interpretability.

CDS frequency (main text)

```{r pl-comp-acc-full, include=FALSE}
model_acc_C_PL_full = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_cds_scaled + 
          group*imageability_scaled*frequency_cds_scaled + 
          (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + 
          (1 | word),
        data = data_pl %>% filter(task == "C"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_C_PL_full)
```

```{r echo = FALSE}
table1 <- tidy(model_acc_C_PL_full, effects = "fixed")
kable(table1, digits = 3)
```

SUBTLEX frequency (supplementary materials)

```{r pl-comp-acc-sup, include=FALSE}
model_acc_C_PL_full_sup = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_scaled + 
          group*imageability_scaled*frequency_scaled + 
          (1 + AoA_scaled + imageability_scaled + frequency_scaled | child_id) + 
          (1 | word),
        data = data_pl %>% filter(task == "C"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_C_PL_full_sup)
```

```{r echo = FALSE}
table2 <- tidy(model_acc_C_PL_full_sup, effects = "fixed")
kable(table2, digits = 3)
```

Compare model with SUBTLEX and CDS
From ChatGPT (but I would verify this) 
Interpretation:
Lower AIC/BIC = better model
ΔAIC:
< 2 = essentially equivalent
4–7 = moderate evidence
10 = strong evidence

In case of comprehension AIC and BIC are smaller (indicating better fit)
CDS is also a *non-significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_acc_C_PL_full_sup, model_acc_C_PL_full)
BIC(model_acc_C_PL_full_sup, model_acc_C_PL_full)
```

#### Production Accuracy

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r pl-prod-acc-1, include=FALSE}
model_acc_P_PL_simple = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_scaled + 
          group*imageability_scaled*frequency_scaled + 
          (1 | child_id) + (1 | word),
        data = data_pl %>% filter(task == "P"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_P_PL_simple)
```

```{r echo = FALSE}
table3 <- tidy(model_acc_P_PL_simple, effects = "fixed")
kable(table3, digits = 3)
```

...Second, with CDS frequency

```{r pl-prod-acc-2, include = FALSE}
model_acc_P_PL_simple_cds = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_cds_scaled + 
          group*imageability_scaled*frequency_cds_scaled + 
          (1 | child_id) + (1 | word),
        data = data_pl %>% filter(task == "P"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_P_PL_simple_cds)
```

```{r echo = FALSE}
table4 <- tidy(model_acc_P_PL_simple_cds, effects = "fixed")
kable(table4, digits = 3)
```

In case of production AIC and BIC are larger (indicating worse fit)
CDS is also a *non-significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_acc_P_PL_simple, model_acc_P_PL_simple_cds)
BIC(model_acc_P_PL_simple, model_acc_P_PL_simple_cds)
```

#### RTs Comprehension

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r pl-comp-rt-1, include=FALSE}
model_rt_C_PL_simple = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_scaled +
                              group * imageability_scaled*frequency_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_pl_out_outliers %>% filter(task == "C"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_C_PL_simple)
```

```{r echo = FALSE}
table5 <- tidy(model_rt_C_PL_simple, effects = "fixed")
kable(table5, digits = 3)
```

...Second, with CDS frequency

```{r pl-comp-rt-2, include = FALSE}
model_rt_C_PL_simple_cds = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              group * imageability_scaled*frequency_cds_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_pl_out_outliers %>% filter(task == "C"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_C_PL_simple_cds)
```

```{r echo = FALSE}
table6 <- tidy(model_rt_C_PL_simple_cds, effects = "fixed")
kable(table6, digits = 3)
```

In case of comprehension RTs AIC and BIC are smaller (indicating better fit)
CDS is also *significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_rt_C_PL_simple, model_rt_C_PL_simple_cds)
BIC(model_rt_C_PL_simple, model_rt_C_PL_simple_cds)
```

#### RTs Production

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r pl-prod-rt-1, include=FALSE}
model_rt_P_PL_simple = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_scaled +
                              group * imageability_scaled*frequency_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_pl_out_outliers %>% filter(task == "P"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_P_PL_simple)
```

```{r echo = FALSE}
table7 <- tidy(model_rt_P_PL_simple, effects = "fixed")
kable(table7, digits = 3)
```

...Second, with CDS frequency

```{r pl-prod-rt-2, include=FALSE}
model_rt_P_PL_simple_cds = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              group * imageability_scaled*frequency_cds_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_pl_out_outliers %>% filter(task == "P"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_P_PL_simple_cds)
```

```{r echo = FALSE}
table6 <- tidy(model_rt_P_PL_simple_cds, effects = "fixed")
kable(table6, digits = 3)
```

In case of production RTs AIC and BIC are similar.
CDS is a *non-significant* predictor of accuracy in production.

```{r echo = FALSE}
AIC(model_rt_P_PL_simple, model_rt_P_PL_simple_cds)
BIC(model_rt_P_PL_simple, model_rt_P_PL_simple_cds)
```

### Norwegian

#### Comprehension Accuracy

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r no-comp-acc-1, include = FALSE}
model_acc_C_NO_simple = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_scaled + 
          group*imageability_scaled*frequency_scaled + 
          (1 | child_id) + (1 | word),
        data = data_no %>% filter(task == "C"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_C_NO_simple)
```

```{r echo = FALSE}
table7 <- tidy(model_acc_C_NO_simple, effects = "fixed")
kable(table7, digits = 3)
```

...Second, with CDS frequency

```{r no-comp-acc-2, include = FALSE}
model_acc_C_NO_simple_cds = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_cds_scaled + 
          group*imageability_scaled*frequency_cds_scaled + 
          (1 | child_id) + (1 | word),
        data = data_no %>% filter(task == "C"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_C_NO_simple_cds)
```

```{r echo = FALSE}
table8 <- tidy(model_acc_C_NO_simple_cds, effects = "fixed")
kable(table8, digits = 3)
```

Compare model with SUBTLEX and CDS
From ChatGPT (but I would verify this) 
Interpretation:
Lower AIC/BIC = better model
ΔAIC:
< 2 = essentially equivalent
4–7 = moderate evidence
10 = strong evidence

In case of comprehension AIC and BIC are smaller (indicating better fit)
CDS is a *non-significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_acc_C_NO_simple, model_acc_C_NO_simple_cds)
BIC(model_acc_C_NO_simple, model_acc_C_NO_simple_cds)
```

#### Production Accuracy

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r no-prod-acc-1, include = FALSE}
model_acc_P_NO_simple = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_scaled + 
          group*imageability_scaled*frequency_scaled + 
          (1 | child_id) + (1 | word),
        data = data_no %>% filter(task == "P"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_P_NO_simple)
```

```{r echo = FALSE}
table9 <- tidy(model_acc_P_NO_simple, effects = "fixed")
kable(table9, digits = 3)
```

...Second, with CDS frequency

```{r no-prod-acc-2, include = FALSE}
model_acc_P_NO_simple_cds = 
  glmer(accuracy_strict ~ 
          group*AoA_scaled + 
          group*imageability_scaled + 
          group*frequency_cds_scaled + 
          group*imageability_scaled*frequency_cds_scaled + 
          (1 | child_id) + (1 | word),
        data = data_no %>% filter(task == "P"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_P_NO_simple_cds)
```

```{r echo = FALSE}
table10 <- tidy(model_acc_P_NO_simple_cds, effects = "fixed")
kable(table10, digits = 3)
```

In case of production AIC and BIC are smaller (indicating better fit)
CDS is also a *non-significant* predictor of accuracy in production.

```{r echo = FALSE}
AIC(model_acc_P_NO_simple, model_acc_P_NO_simple_cds)
BIC(model_acc_P_NO_simple, model_acc_P_NO_simple_cds)
```

#### RTs Comprehension

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r no-comp-rt-1, include = FALSE}
model_rt_C_NO_simple = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_scaled +
                              group * imageability_scaled*frequency_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_no_out_outliers %>% filter(task == "C"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_C_NO_simple)
```

```{r echo = FALSE}
table11 <- tidy(model_rt_C_NO_simple, effects = "fixed")
kable(table11, digits = 3)
```

...Second, with CDS frequency

```{r no-comp-rt-2, include = FALSE}
model_rt_C_NO_simple_cds = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              group * imageability_scaled*frequency_cds_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_no_out_outliers %>% filter(task == "C"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_C_NO_simple_cds)
```

```{r}
table12 <- tidy(model_rt_C_NO_simple_cds, effects = "fixed")
kable(table12, digits = 3)
```

In case of comprehension RTs AIC and BIC are smaller (indicating better fit)
CDS is also *non-significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_rt_C_NO_simple, model_rt_C_NO_simple_cds)
BIC(model_rt_C_NO_simple, model_rt_C_NO_simple_cds)
```

#### RTs Production

First, with SUBTLEX frequency...
(I'm showing only simple models)

```{r no-prod-rt-1, include = FALSE}
model_rt_P_NO_simple = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_scaled +
                              group * imageability_scaled*frequency_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_no_out_outliers %>% filter(task == "P"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_P_NO_simple)
```

```{r echo = FALSE}
table13 <- tidy(model_rt_P_NO_simple, effects = "fixed")
kable(table13, digits = 3)
```

...Second, with CDS frequency

```{r no-prod-rt-2, include = FALSE}
model_rt_P_NO_simple_cds = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              group * imageability_scaled*frequency_cds_scaled + 
                              (1 | child_id) + (1 | word),
                          data = data_no_out_outliers %>% filter(task == "P"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5))
)
                       
summary(model_rt_P_NO_simple_cds)
```

```{r echo = FALSE}
table15 <- tidy(model_rt_P_NO_simple_cds, effects = "fixed")
kable(table15, digits = 3)
```

In case of production RTs AIC and BIC are smaller (indicating better fit).
CDS is a *non-significant* predictor of accuracy in production.

```{r echo=FALSE}
AIC(model_rt_P_NO_simple, model_rt_P_NO_simple_cds)
BIC(model_rt_P_NO_simple, model_rt_P_NO_simple_cds)
```


##  Age effects

##  Polish comprehension

```{r}
#scale and center age
data_pl$Age_scaled <- scale(data_pl$Age, center = T, scale = T)

model_acc_C_PL_simple_age = 
  glmer(accuracy_strict ~ group*(AoA_scaled + imageability_scaled + frequency_cds_scaled) +
          Age_scaled*(AoA_scaled + imageability_scaled + frequency_cds_scaled) +
          (1 | child_id) + (1 | word),
        data = data_pl %>% filter(task == "C"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_C_PL_simple_age)
```

##  Polish production

```{r}
model_acc_P_PL_simple_age = 
  glmer(accuracy_strict ~ group*(AoA_scaled + 
                                   imageability_scaled + frequency_cds_scaled) +
          Age_scaled*(AoA_scaled + 
                        imageability_scaled + 
                        frequency_cds_scaled) +
          (1 | child_id) + (1 | word),
        data = data_pl %>% filter(task == "P"),
        family = binomial,
        control = glmerControl(optimizer = "bobyqa",
                               optCtrl = list(maxfun= 2e5)))
                       
summary(model_acc_P_PL_simple_age)
```

