---
title: "BLC CLT and Word Properties"
date: "2026-04-01"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
options(scipen = 999) #removes scietific notation
```

```{r libraries, include=FALSE}
library(tidyverse)
library(Hmisc)
library(lme4)
library(broom.mixed)
library(afex)
library(gtsummary)
library(flextable)
library(officer)
library(simr)
library(MuMIn)
library(parameters)
library(patchwork)
library(car)
```

```{r data, include=FALSE}
data_pl <- read_csv("data_clt_wp_pl_anon.csv")
data_no <- read_csv("data_clt_wp_no_anon.csv")
```

## Data prepation

Step 1. Removing outliers from RTs
Outliers are defined as RTs that are both higher 
than mean RT + 3SD of a given child in a given task 
AND mean RT + 3SD of a given task

Database filtered for complete datapoints (frequency), 
correct responses and measured RTs higher than 1000 ms 
(lower are typically measurement errors)

Step 2. Scaling

```{r outliers-rts-pl, include=FALSE}
data_pl_filtered <- data_pl %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
#excluded RTs < 1000 ms
data_pl %>% filter(reaction_time < 1000) %>% summarise(n()) #132
#there are 11173 measured reaction times for correct responses and complete cases 
mean_RT_PL <- data_pl_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_PL <- mean_RT_PL %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_pl_with_outliers <- data_pl_filtered %>%
  left_join(mean_RT_PL, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_pl_meanRTs <- data_pl_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), 
            .groups = "drop")

data_pl_with_outliers <- data_pl_with_outliers %>%
  left_join(data_pl_meanRTs , by = "task") %>%
  mutate(outlier_overall = (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_PL <- data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_PL)

#Now we exclude outliers from the database based on the two criteria 
#(>M+3SD for child and for task)
#This database will be used for the analyses of the reaction times
data_pl_out_outliers <- data_pl_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#excluded RTs
data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE) %>%
  summarise(n()) #90
```

```{r scale-pl, include=FALSE}
#data without RT outliers for RT analyses
#frequency is on a log scale but frequency cds needs to be transformed
data_pl_out_outliers <- data_pl_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds),
                                     center = T, scale = T),
    frequency_scaled = scale(FrequencyLemmaLog, 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time),
    Age_scaled = scale(Age, center = T, scale = T))

data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#data with RT outliers for accuracy analyses
data_pl <- data_pl %>%
  mutate(
     frequency_cds_scaled = scale(log(frequency_cds+1), 
                                      center = T, scale = T),
     frequency_scaled = scale(FrequencyLemmaLog, 
                              center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE),
    Age_scaled = scale(Age, center = T, scale = T))

summary(data_pl)
data_pl$group <-relevel(factor(data_pl$group), ref="monoPL")
```

```{r outliers-rts-no, include=FALSE}
data_no_filtered <- data_no %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_no_filtered$reaction_time)  
#excluded RTs < 1000 ms
data_no %>% filter(reaction_time < 1000) %>% summarise(n()) #196
#there are 9850 measured reaction times for correct responses and complete cases,
#RTs>=1000 ms
  
mean_RT_NOR <- data_no_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_NOR <- mean_RT_NOR %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_no_with_outliers <- data_no_filtered %>%
  left_join(mean_RT_NOR, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = 
           (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_no_meanRTs <- data_no_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), .groups = "drop")

data_no_with_outliers <- data_no_with_outliers %>%
  left_join(data_no_meanRTs , by = "task") %>%
  mutate(outlier_overall = 
           (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_no <- data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_no)

#Now we exclude outliers from the database based on the two criteria 
#(>M+3SD for child and for task)
data_no_out_outliers <- data_no_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
#excluded RTs
data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE) %>%
  summarise(n()) #77
```

NO CDS frequency is scaled on the formula:
ln(x+1) (bc there are same frequencies = 0)

```{r scale-no, include=FALSE}
data_no_out_outliers <- data_no_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = T, scale = T),
    frequency_scaled = scale(log(Frequency), 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time),
    Age_scaled = scale(Age, center = T, scale = T))

data_no_out_outliers$group <-relevel(factor(data_no_out_outliers$group), ref="monoNO")

#and for accuracy analyses we only need to scale the variables, no outliers
data_no <- data_no %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = T, scale = T),
    frequency_scaled = scale(log(Frequency + 1), 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, center = T, 
                                scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    Age_scaled = scale(Age, center = T, scale = T))

data_no$group <-relevel(factor(data_no$group), ref="monoNO")
```

## Correlations between word properties

### Polish

```{r pl-correlation, include = FALSE}
df_num_pl <- data_pl %>%
  distinct(word, frequency_cds_scaled, 
           imageability_scaled, 
           AoA_scaled) %>%
  select(-word)
df_num_pl$freq_imag <- df_num_pl$frequency_cds_scaled * df_num_pl$imageability_scaled
cor_res <- rcorr(as.matrix(df_num_pl), type = "spearman")
cor_res
# correlation matrix
cor_res$r
# p-values
cor_res$P
#degrees of freedom
cor_res$n - 2
```

### Norwegian

```{r no-correlation, include = FALSE}
df_num_no <- data_no %>%
  distinct(word, frequency_cds_scaled, 
           imageability_scaled, AoA_scaled) %>%
  select(-word)
df_num_no$freq_imag <- df_num_no$frequency_cds_scaled * df_num_no$imageability_scaled
cor_res_no <- rcorr(as.matrix(df_num_no), type = "spearman")
cor_res_no
# correlation matrix
cor_res_no$r
# p-values
cor_res_no$P
#degrees of freedom
cor_res_no$n - 2
```

## Accuracy Models

We run all models together (divided only into accuracy and RTs):

1) Bind Polish and Norwegian data (with outliers)
2) Run and view accuracy models
3) Summarise the results

### Bind data

```{r bind data, include = FALSE}
bind_rows(data_pl, data_no) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full
```

### Prepare models

```{r models-accuracy-all, echo = FALSE}
formula_glmer <- accuracy_strict ~ 
  Age_scaled +
  group * (AoA_scaled + 
             imageability_scaled + 
             frequency_cds_scaled) +
  imageability_scaled * frequency_cds_scaled +
  (1 + AoA_scaled + 
     imageability_scaled + 
     frequency_cds_scaled | child_id) +
  (1 | word)

ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_acc    = list(language = "POLISH",    task = "P"),
  polish_c_acc    = list(language = "POLISH",    task = "C"),
  norwegian_p_acc = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_acc = list(language = "NORWEGIAN", task = "C")
)

models_acc <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full, language == cond$language & task == cond$task)
  model <- glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)
  
  #create a an oject in the global environment (for R2 calculation)
  data_name <- paste0("data_", cond$language, "_", cond$task)
  assign(data_name, df_sub, envir = globalenv())
  model@call$data <- as.name(data_name)
  
  model
})

# models
summary(models_acc)
```

Check convergence:
No warnings.

```{r convergence-acc-checks, echo = FALSE}
lapply(models_acc, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r, echo = FALSE}
#summary(models_acc$polish_c_acc)
tidy(models_acc$polish_c_acc, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
r.squaredGLMM(models_acc$polish_c_acc)
vif(models_acc$polish_c_acc)
#we consider theoretical R 
#(not impacted by the lack of convergence of the null model)
```

### Polish Production

```{r, echo = FALSE}
#summary(models_acc$polish_p_acc)
tidy(models_acc$polish_p_acc, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
r.squaredGLMM(models_acc$polish_p_acc)
vif(models_acc$polish_p_acc)
#we consider theoretical R 
#(not impacted by the lack of convergence of the null model)
```

### Norwegian Comprehension

```{r, echo = FALSE}
#summary(models_acc$norwegian_c_acc)
tidy(models_acc$norwegian_c_acc, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
r.squaredGLMM(models_acc$norwegian_c_acc)
vif(models_acc$norwegian_c_acc)
#we consider theoretical R 
#(not impacted by the lack of convergence of the null model)
```

### Norwegian Production

```{r, echo = FALSE}
#summary(models_acc$norwegian_p_acc)
tidy(models_acc$norwegian_p_acc, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
r.squaredGLMM(models_acc$norwegian_p_acc)
vif(models_acc$norwegian_p_acc)
#we consider theoretical R 
#(not impacted by the lack of convergence of the null model)
```

##  RTs models

### Bind data

```{r bind-rt-data}
bind_rows(data_pl_out_outliers, data_no_out_outliers) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full_out_outliers
```

### Prepare all models

First more complex with random slopes:

```{r models-rts-all, eval = FALSE}
formula_lmer <- logRT ~ Age_scaled + 
  group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        imageability_scaled * frequency_cds_scaled +
                        (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + 
  (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt)
```

Most models did not converge: _boundary (singular) fit_

```{r convergence-rt-checks, include = FALSE, eval = FALSE}
lapply(models_rt, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

We proceed with simpler models (no random slopes)

```{r models-rts-all-simple, echo = FALSE}
formula_lmer_simpler <- logRT ~ Age_scaled + 
  group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
  imageability_scaled * frequency_cds_scaled +
  (1 | child_id) + (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt_simpler <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer_simpler, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt_simpler)
```

```{r convergence-rt-checks-2, echo = FALSE}
lapply(models_rt_simpler, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r, echo = FALSE}
#summary(models_rt_simpler$polish_c_rt)
tidy(models_rt_simpler$polish_c_rt, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_simpler$polish_c_rt)
r.squaredGLMM(models_rt_simpler$polish_c_rt)
```

### Polish Production

```{r}
#summary(models_rt_simpler$polish_p_rt)
tidy(models_rt_simpler$polish_p_rt, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_simpler$polish_p_rt)
r.squaredGLMM(models_rt_simpler$polish_p_rt)
```

### Norwegian Comprehension

```{r}
#summary(models_rt_simpler$norwegian_c_rt)
tidy(models_rt_simpler$norwegian_c_rt, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_simpler$norwegian_c_rt)
r.squaredGLMM(models_rt_simpler$norwegian_c_rt)
```

### Norwegian Production

```{r}
#summary(models_rt_simpler$norwegian_p_rt)
tidy(models_rt_simpler$norwegian_p_rt, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_simpler$norwegian_p_rt)
r.squaredGLMM(models_rt_simpler$norwegian_p_rt)
```

# Exposure and Accuracy

###  Select bilinguals

```{r select-bi}
data_full %>% filter(group == "bi") -> data_bi_full
```

```{r explore-exposure}
data_bi_full %>% 
  distinct(child_id, no_input_sum_percentage) %>%
  ggplot(aes(x = no_input_sum_percentage)) +
  geom_density()
  
data_bi_full %>% 
  distinct(child_id, pl_input_sum_percentage) %>%
  ggplot(aes(x = pl_input_sum_percentage)) +
  geom_density()
```

### Prepare all models

```{r exposure-accuracy-models, include = FALSE}
conditions <- list(
  polish_p_exposure    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)



subsets_acc_exposure <- lapply(conditions, function(cond) {
  subset(data_bi_full, language == cond$language & task == cond$task)
})

ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

models_acc_exposure <- lapply(names(conditions), function(nm) {
  cond   <- conditions[[nm]]
  df_sub <- subsets_acc_exposure[[nm]]

  formula_glmer <- as.formula(paste0(
    "accuracy_strict ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + (1 | word)"
  ))

  model <- glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)

  # repoint the stored data reference at the stable list element
  model@call$data <- bquote(subsets_acc_exposure[[.(nm)]])

  model
})
names(models_acc_exposure) <- names(conditions)
summary(models_acc_exposure)
```

```{r convergence-acc-exposure-checks}
lapply(models_acc_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r echo = FALSE}
summary(models_acc_exposure$polish_c_exposure)
tidy(models_acc_exposure$polish_c_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_acc_exposure$polish_c_exposure)
r.squaredGLMM(models_acc_exposure$polish_c_exposure)
```
 
### Polish Production

```{r echo = FALSE}
#summary(models_acc_exposure$polish_p_exposure)
tidy(models_acc_exposure$polish_p_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_acc_exposure$polish_p_exposure)
r.squaredGLMM(models_acc_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r echo = FALSE}
#summary(models_acc_exposure$norwegian_c_exposure)
tidy(models_acc_exposure$norwegian_c_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_acc_exposure$norwegian_c_exposure)
r.squaredGLMM(models_acc_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r echo = FALSE}
#summary(models_acc_exposure$norwegian_p_exposure)
tidy(models_acc_exposure$norwegian_p_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_acc_exposure$norwegian_p_exposure)
r.squaredGLMM(models_acc_exposure$norwegian_p_exposure)
``` 

# Exposure and RTs

```{r select-bi-no-outliers}
data_full_out_outliers %>% filter(group == "bi") -> data_bi_full_rt
```

```{r exposure-rt-models, include = FALSE}
conditions <- list(
  polish_p_exposure_rt    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure_rt    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure_rt = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure_rt = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

models_rt_exposure <- lapply(conditions, function(cond) {
  df_sub <- subset(data_bi_full_rt, language == cond$language & task == cond$task)
  
  formula_lmer <- as.formula(paste0(
    "logRT ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 | child_id) + (1 | word)"
  ))
  
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})
```

```{r convergence-rt-exposure-checks, echo = FALSE}
lapply(models_rt_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r echo = FALSE}
#summary(models_rt_exposure$polish_c_exposure)
tidy(models_rt_exposure$polish_c_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_exposure$polish_c_exposure)
r.squaredGLMM(models_rt_exposure$polish_c_exposure)
```
 
 
 
```{r}

```

### Polish Production

```{r echo = FALSE}
#summary(models_rt_exposure$polish_p_exposure)
tidy(models_rt_exposure$polish_p_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
r.squaredGLMM(models_rt_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r echo = FALSE}
#summary(models_rt_exposure$norwegian_c_exposure)
tidy(models_rt_exposure$norwegian_c_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3))
vif(models_rt_exposure$norwegian_c_exposure)
r.squaredGLMM(models_rt_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r echo = FALSE}
#summary(models_rt_exposure$norwegian_p_exposure)
tidy(models_rt_exposure$norwegian_p_exposure, effects = "fixed", 
     conf.int = TRUE, conf.level = 0.95) %>%
  mutate (estimate = round(estimate, 3),
          std.error = round(std.error,3),
          statistic = round(statistic,3),
          p.value = round(p.value,3)) %>% arrange(match(term, order_no)) %>% View()
vif(models_rt_exposure$norwegian_p_exposure)
r.squaredGLMM(models_rt_exposure$norwegian_p_exposure)
``` 

# Reliability analyses
## Accuracy
### Polish production

```{r}
data_pl_P <- subset(data_pl, task == "P")

data_wide_PL_P <- data_pl_P %>%
  select(child_id, word, accuracy_strict) %>%
  pivot_wider(names_from = word, values_from = accuracy_strict)

data_for_alpha_PL_P <- data_wide_PL_P[, -1]

alpha_PL_P <- psych::alpha(data_for_alpha_PL_P, check.keys = FALSE)

print(alpha_PL_P$total$raw_alpha)
``` 

``` {r}
cat("Cronbach's alpha for Polish Production:", round(alpha_PL_P$total$raw_alpha,2), "\n")
```

``` {r}
items_PL_P <- colnames(data_for_alpha_PL_P)
half1_PL_P <- sample(items_PL_P, length(items_PL_P)/2)
half2_PL_P <- setdiff(items_PL_P, half1_PL_P)

score_half1_PL_P <- rowSums(data_for_alpha_PL_P[, half1_PL_P], na.rm = TRUE)
score_half2_PL_P  <- rowSums(data_for_alpha_PL_P[, half2_PL_P], na.rm = TRUE)

r_PL_P <- cor(score_half1_PL_P, score_half2_PL_P, use = "pairwise.complete.obs")

r_corr_PL_P <- (2 * r_PL_P) / (1 + r_PL_P)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for Polish Production:", round(r_corr_PL_P, 2), "\n")
```

### Polish comprehension
``` {r} 
data_pl_C <- subset(data_pl, task == "C")

data_wide_PL_C <- data_pl_C %>%
  select(child_id, word, accuracy_strict) %>%
  pivot_wider(names_from = word, values_from = accuracy_strict)

data_for_alpha_PL_C <- data_wide_PL_C[, -1]
```

```{r}
alpha_PL_C <- psych::alpha(data_for_alpha_PL_C, check.keys = FALSE)

print(alpha_PL_C$total$raw_alpha)
```

```{r}
cat("Cronbach's alpha for Polish Comprehension:", round(alpha_PL_C$total$raw_alpha,2), "\n")
```

``` {r}
items_PL_C <- colnames(data_for_alpha_PL_C)
half1_PL_C <- sample(items_PL_C, length(items_PL_C)/2)
half2_PL_C <- setdiff(items_PL_C, half1_PL_C)

score_half1_PL_C <- rowSums(data_for_alpha_PL_C[, half1_PL_C], na.rm = TRUE)
score_half2_PL_C  <- rowSums(data_for_alpha_PL_C[, half2_PL_C], na.rm = TRUE)

r_PL_C <- cor(score_half1_PL_C, score_half2_PL_C, use = "pairwise.complete.obs")

r_corr_PL_C <- (2 * r_PL_C) / (1 + r_PL_C)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for Polish Comprehension:", round(r_corr_PL_C, 2), "\n")
```

### Norwegian production

``` {r} 
data_no_P <- subset(data_no, task == "P")

data_wide_NOR_P <- data_no_P %>%
  select(child_id, word, accuracy_strict) %>%
  pivot_wider(names_from = word, values_from = accuracy_strict)

data_for_alpha_NOR_P <- data_wide_NOR_P[, -1]

alpha_NOR_P <- psych::alpha(data_for_alpha_NOR_P, check.keys = FALSE)

print(alpha_NOR_P$total$raw_alpha)
```

``` {r}
cat("Cronbach's alpha for Norwegian Production:", round(alpha_NOR_P$total$raw_alpha,2), "\n")
```

``` {r}
items_NOR_P <- colnames(data_for_alpha_NOR_P)
half1_NOR_P <- sample(items_NOR_P, length(items_NOR_P)/2)
half2_NOR_P <- setdiff(items_NOR_P, half1_NOR_P)

score_half1_NOR_P <- rowSums(data_for_alpha_NOR_P[, half1_NOR_P], na.rm = TRUE)
score_half2_NOR_P  <- rowSums(data_for_alpha_NOR_P[, half2_NOR_P], na.rm = TRUE)

r_NOR_P <- cor(score_half1_NOR_P, score_half2_NOR_P, use = "pairwise.complete.obs")

r_corr_NOR_P <- (2 * r_NOR_P) / (1 + r_NOR_P)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for Norwegian Production:", round(r_corr_NOR_P, 2), "\n")
```

### Norwegian comprehension

``` {r}
data_no_C <- subset(data_no, task == "C")

data_wide_NOR_C <- data_no_C %>%
  select(child_id, word, accuracy_strict) %>%
  pivot_wider(names_from = word, values_from = accuracy_strict)

data_for_alpha_NOR_C <- data_wide_NOR_C[, -1]

alpha_NOR_C <- psych::alpha(data_for_alpha_NOR_C, check.keys = FALSE)

print(alpha_NOR_C$total$raw_alpha)
```

``` {r}
cat("Cronbach's alpha for Norwegian Comprehension:", round(alpha_NOR_C$total$raw_alpha,2), "\n")
```

``` {r}
items_NOR_C <- colnames(data_for_alpha_NOR_C)
half1_NOR_C <- sample(items_NOR_C, length(items_NOR_C)/2)
half2_NOR_C <- setdiff(items_NOR_C, half1_NOR_C)

score_half1_NOR_C <- rowSums(data_for_alpha_NOR_C[, half1_NOR_C], na.rm = TRUE)
score_half2_NOR_C  <- rowSums(data_for_alpha_NOR_C[, half2_NOR_C], na.rm = TRUE)

r_NOR_C <- cor(score_half1_NOR_C, score_half2_NOR_C, use = "pairwise.complete.obs")

r_corr_NOR_C <- (2 * r_NOR_C) / (1 + r_NOR_C)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for Norwegian Comprehension:", round(r_corr_NOR_C, 2), "\n")
```

## Reaction times
### Polish comprehension RTs

``` {r}
data_PL_C_RT <- subset(data_pl_out_outliers, task == "C")

data_wide_PL_C_RT <- data_PL_C_RT %>%
  select(child_id, word, logRT) %>%
  pivot_wider(names_from = word, values_from = logRT)

data_for_sh_PL_C_RT <- data_wide_PL_C_RT[, -1]
```

``` {r}
items_PL_C_RT <- colnames(data_for_sh_PL_C_RT)
half1_PL_C_RT <- sample(items_PL_C_RT, length(items_PL_C_RT)/2)
half2_PL_C_RT <- setdiff(items_PL_C_RT, half1_PL_C_RT)

score_half1_PL_C_RT <- rowSums(data_for_sh_PL_C_RT[, half1_PL_C_RT], na.rm = TRUE)
score_half2_PL_C_RT  <- rowSums(data_for_sh_PL_C_RT[, half2_PL_C_RT], na.rm = TRUE)

r_PL_C_RT <- cor(score_half1_PL_C_RT, score_half2_PL_C_RT, use = "pairwise.complete.obs")

r_corr_PL_C_RT <- (2 * r_PL_C_RT) / (1 + r_PL_C_RT)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for RTs in Polish Comprehension:", round(r_corr_PL_C_RT, 2), "\n")
```

### Polish production RTs

``` {r}
data_PL_P_RT <- subset(data_pl_out_outliers, task == "P")

data_wide_PL_P_RT <- data_PL_P_RT %>%
  select(child_id, word, logRT) %>%
  pivot_wider(names_from = word, values_from = logRT)

data_for_sh_PL_P_RT <- data_wide_PL_P_RT[, -1]
```

``` {r}
items_PL_P_RT <- colnames(data_for_sh_PL_P_RT)
half1_PL_P_RT <- sample(items_PL_P_RT, length(items_PL_P_RT)/2)
half2_PL_P_RT <- setdiff(items_PL_P_RT, half1_PL_P_RT)

score_half1_PL_P_RT <- rowSums(data_for_sh_PL_P_RT[, half1_PL_P_RT], na.rm = TRUE)
score_half2_PL_P_RT  <- rowSums(data_for_sh_PL_P_RT[, half2_PL_P_RT], na.rm = TRUE)

r_PL_P_RT <- cor(score_half1_PL_P_RT, score_half2_PL_P_RT, use = "pairwise.complete.obs")

r_corr_PL_P_RT <- (2 * r_PL_P_RT) / (1 + r_PL_P_RT)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for RTs in Polish Production:", round(r_corr_PL_P_RT, 2), "\n")
```

### Norwegian production RTs

``` {r}
data_NOR_P_RT <- subset(data_no_out_outliers, task == "P")

data_wide_NOR_P_RT <- data_NOR_P_RT %>%
  select(child_id, word, logRT) %>%
  pivot_wider(names_from = word, values_from = logRT)

data_for_sh_NOR_P_RT <- data_wide_NOR_P_RT[, -1]
```

``` {r}
items_NOR_P_RT <- colnames(data_for_sh_NOR_P_RT)
half1_NOR_P_RT <- sample(items_NOR_P_RT, length(items_NOR_P_RT)/2)
half2_NOR_P_RT <- setdiff(items_NOR_P_RT, half1_NOR_P_RT)

score_half1_NOR_P_RT <- rowSums(data_for_sh_NOR_P_RT[, half1_NOR_P_RT], na.rm = TRUE)
score_half2_NOR_P_RT  <- rowSums(data_for_sh_NOR_P_RT[, half2_NOR_P_RT], na.rm = TRUE)

r_NOR_P_RT <- cor(score_half1_NOR_P_RT, score_half2_NOR_P_RT, use = "pairwise.complete.obs")

r_corr_NOR_P_RT <- (2 * r_NOR_P_RT) / (1 + r_NOR_P_RT)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for RTs in Norwegian Production:", round(r_corr_NOR_P_RT, 2), "\n")
```

### Norwegian comprehension RTs

``` {r}
data_NOR_C_RT <- subset(data_no_out_outliers, task == "C")

data_wide_NOR_C_RT <- data_NOR_C_RT %>%
  select(child_id, word, logRT) %>%
  pivot_wider(names_from = word, values_from = logRT)

data_for_sh_NOR_C_RT <- data_wide_NOR_C_RT[, -1]
```


``` {r}
items_NOR_C_RT <- colnames(data_for_sh_NOR_C_RT)
half1_NOR_C_RT <- sample(items_NOR_C_RT, length(items_NOR_C_RT)/2)
half2_NOR_C_RT <- setdiff(items_NOR_C_RT, half1_NOR_C_RT)

score_half1_NOR_C_RT <- rowSums(data_for_sh_NOR_C_RT[, half1_NOR_C_RT], na.rm = TRUE)
score_half2_NOR_C_RT  <- rowSums(data_for_sh_NOR_C_RT[, half2_NOR_C_RT], na.rm = TRUE)

r_NOR_C_RT <- cor(score_half1_NOR_C_RT, score_half2_NOR_C_RT, use = "pairwise.complete.obs")

r_corr_NOR_C_RT <- (2 * r_NOR_C_RT) / (1 + r_NOR_C_RT)
```

``` {r}
cat("Split-half reliability (Spearman-Brown corrected) for RTs in Norwegian Comprehension:", round(r_corr_NOR_C_RT, 2), "\n")
```

# Correlations between tasks + accuracy and RTs
## Polish
``` {r}
data_total_PL <- data_pl %>%
  left_join(data_pl_out_outliers %>%
              select(child_id, word, task, logRT),
            by = c("child_id", "word", "task"))

scores_PL <- data_total_PL %>%
  group_by(child_id, task) %>%
  summarise(
    acc = mean(accuracy_strict, na.rm = TRUE),
    rt = mean(logRT, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  tidyr::pivot_wider(names_from = task, values_from = c(acc, rt))
```

``` {r}
psych::corr.test(scores_PL[, c("acc_P", "acc_C", "rt_P", "rt_C")],
                 method = "spearman", use = "pairwise")

psych::corr.test(scores_PL[, c("acc_P", "acc_C", "rt_P", "rt_C")],
                 method = "spearman", use = "pairwise")$p
```

## Norwegian

``` {r}
data_total_no <- data_no %>%
  left_join(data_no_out_outliers %>%
              select(child_id, word, task, logRT),
            by = c("child_id", "word", "task"))

scores_NOR <- data_total_no %>%
  group_by(child_id, task) %>%
  summarise(
    acc = mean(accuracy_strict, na.rm = TRUE),
    rt = mean(logRT, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  tidyr::pivot_wider(names_from = task, values_from = c(acc, rt))
```

``` {r}
psych::corr.test(scores_NOR[, c("acc_P", "acc_C", "rt_P", "rt_C")],
                 method = "spearman", use = "pairwise")

psych::corr.test(scores_NOR[, c("acc_P", "acc_C", "rt_P", "rt_C")],
                 method = "spearman", use = "pairwise")$p
```

## Bilinguals: Polish vs Norwegian

``` {r}
common_children <- intersect(unique(data_total_PL$child_id),
                             unique(data_total_no$child_id))
length(common_children)
data_PL_common <- filter(data_total_PL, child_id %in% common_children)
data_no_common <- filter(data_total_no, child_id %in% common_children)

bi_scores_PL <- data_PL_common %>%
  group_by(child_id, task) %>%
  summarise(acc = mean(accuracy_strict, na.rm = TRUE),
            rt = mean(logRT, na.rm = TRUE),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = task, values_from = c(acc, rt), names_prefix = "PL_")

bi_scores_no <- data_no_common %>%
  group_by(child_id, task) %>%
  summarise(acc = mean(accuracy_strict, na.rm = TRUE),
            rt = mean(logRT, na.rm = TRUE),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = task, values_from = c(acc, rt), names_prefix = "NOR_")

bi_scores_all <- left_join(bi_scores_PL, bi_scores_no, by = "child_id")
```

### Accuracy in production

``` {r}
cor.test(bi_scores_all$acc_PL_P, bi_scores_all$acc_NOR_P, method = "spearman")
```

### Accuracy in comprehension

``` {r}
cor.test(bi_scores_all$acc_PL_C, bi_scores_all$acc_NOR_C, method = "spearman")
```

### RTs in production

``` {r}
cor.test(bi_scores_all$rt_PL_P, bi_scores_all$rt_NOR_P, method = "spearman")
```

### RTs in comprehension

``` {r}
cor.test(bi_scores_all$rt_PL_C, bi_scores_all$rt_NOR_C, method = "spearman")
```
  
# Power analysis

## Accuracy

We conduct analyses on a simpler model - without random slopes -
more similar to the one in Łuniewska et al. (2022).

Some effects were reveresed since in Łuniewska et al. (2022)
baseline for group was "bilingual"

```{r acc-model-power}
acc_model_power <- glmer(accuracy_strict ~ 
                       group * (AoA_scaled + 
                                  imageability_scaled + 
                                  frequency_cds_scaled) + 
                         imageability_scaled*frequency_cds_scaled +
                       (1 | child_id) +
                       (1 | word),
                            data = data_full %>% filter(language == "POLISH" & task == "P"),
                            family = binomial,
                            control = glmerControl(optimizer = "bobyqa", 
                                                   optCtrl = list(maxfun = 2e5)))
summary(acc_model_power)
```

```{r effects-acc}
#two separate vectors bc group is "group" in the model and "groupbi" in the results
lit_effects_acc <- list(
  fixef_name  = c("groupbi",                     
                  "AoA_scaled",      
                  "imageability_scaled",   
                  "frequency_cds_scaled",   
                  "groupbi:frequency_cds_scaled"),
  test_name   = c("group",                        
                  "AoA_scaled",      
                  "imageability_scaled",   
                  "frequency_cds_scaled",   
                  "group:frequency_cds_scaled"),
  effect_size = c(-0.66, #reversed                        
                  -1.02,            
                  0.73,                 
                  0.38,                  
                  0.20) #reversed
)

pwr_results_acc <- list()

for (i in seq_along(lit_effects_acc$fixef_name)) {
  
  fixef_name  <- lit_effects_acc$fixef_name[i]
  test_name   <- lit_effects_acc$test_name[i]
  effect_size <- lit_effects_acc$effect_size[i]
  
  cat("\n>>> Running power simulation for:", fixef_name, "\n")
  
  model_tmp <- acc_model_power
  
  if (!fixef_name %in% names(fixef(model_tmp))) {
    warning("Coefficient not found: ", fixef_name, " — skipping.")
    next
  }
  
  fixef(model_tmp)[fixef_name] <- effect_size
  
  pwr_results_acc[[fixef_name]] <- powerSim(
    model_tmp,
    test = fixed(fixef_name, method = "z"),
    nsim = 1000,
    seed = 42
  )
  
  print(pwr_results_acc[[fixef_name]])
}

beepr::beep(sound = 1)
```

### Power analysis frequency x imageability

```{r pa-freq-im}
# Use the literature-derived effect, with sign matching your hypothesis
fixef(acc_model_power)["imageability_scaled:frequency_cds_scaled"] <- 0.38

#power analysis
pwr_analysis_freq_im <- powerSim(acc_model_power, 
         test = fixed("imageability_scaled:frequency_cds_scaled", method = "z"),
         nsim = 1000,
         seed = 42)
pwr_analysis_freq_im
beepr::beep(sound = 1)
```

## RTs

```{r rt-power-model}
#model
#with raw RTs to match the ones in Łuniewska et al.
model_power_rt <- lme4::lmer(reaction_time ~ 
                       group * (AoA_scaled + 
                                  imageability_scaled + 
                                  frequency_cds_scaled) + 
                       (1 | child_id) +
                       (1 | word),
                            data = data_full_out_outliers %>% filter(language == "POLISH" & task == "P"),
                            control = lmerControl(optimizer = "bobyqa", 
                                                   optCtrl = list(maxfun = 2e5)))
summary(model_power_rt)
fixef(model_power_rt)
```

```{r effects-rts}
#two separate vectors bc group is "group" in the model and "groupbi" in the results
lit_effects_rts <- list(
  fixef_name  = c("groupbi",                     
                  "AoA_scaled",      
                  "imageability_scaled",   
                  "frequency_cds_scaled",   
                  "groupbi:imageability_scaled",   
                  "groupbi:frequency_cds_scaled"),
  test_name   = c("group",                        
                  "AoA_scaled",      
                  "imageability_scaled",   
                  "frequency_cds_scaled",   
                  "group:imageability_scaled",      
                  "group:frequency_cds_scaled"),
  effect_size = c(385.44,                         
                  270.16,            
                  -256.32,                 
                  -189.82,                  
                  -219.02,                          
                  134.81)
)

pwr_results_rt <- list()

for (i in seq_along(lit_effects_rts$fixef_name)) {
  
  fixef_name  <- lit_effects_rts$fixef_name[i]
  test_name   <- lit_effects_rts$test_name[i]
  effect_size <- lit_effects_rts$effect_size[i]
  
  cat("\n>>> Running power simulation for:", fixef_name, "\n")
  
  model_tmp <- model_power_rt
  
  if (!fixef_name %in% names(fixef(model_tmp))) {
    warning("Coefficient not found: ", fixef_name, " — skipping.")
    next
  }
  
  fixef(model_tmp)[fixef_name] <- effect_size
  
  pwr_results_rt[[fixef_name]] <- powerSim(
    model_tmp,
    test = fixed(fixef_name, method = "t"),
    nsim = 1000,
    seed = 42
  )
  
  print(pwr_results_rt[[fixef_name]])
}

beepr::beep(sound = 1)
```

# Visualisations

## Polish

###  Accuracy Comprehension

```{r pl-acc-comp-plot}

acc_PL_C_p1 <- ggplot(data_pl %>% filter(task == "C"), 
             aes(x = AoA, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(
    name = "Accuracy (%)",
    limits = c(0, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  labs(x = "AoA (in years)") +
  theme_minimal()


acc_PL_C_p2 <- ggplot(data_pl %>% filter(task == "C"), 
             aes(x = Imageability, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Imageability (0 to 7)") +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  theme_minimal()+
  theme(legend.position = "none")

acc_PL_C_p3 <- ggplot(data_pl %>% filter(task == "C"), 
             aes(x = frequency_cds_scaled, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
  labs(x= "Scaled CDS log-frequency") +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  theme_minimal() +
  theme(legend.position = "none")

(acc_PL_C_p1 | acc_PL_C_p2 | acc_PL_C_p3) + plot_annotation(title = "Polish Comprehension") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

###  Accuracy Production

```{r pl-acc-prod-plot}
acc_PL_P_p1 <- ggplot(data_pl %>% filter(task == "P"), 
                      aes(x = AoA, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(
    name = "Accuracy (%)",
    limits = c(0, 1),
    labels = scales::percent_format(accuracy = 1)
  ) +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  labs(x = "AoA (in years)") +
  theme_minimal()


acc_PL_P_p2 <- ggplot(data_pl %>% filter(task == "P"), 
                      aes(x = Imageability, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
  labs(x = "Imageability (0 to 7)") +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  theme_minimal()+
  theme(legend.position = "none")

acc_PL_P_p3 <- ggplot(data_pl %>% filter(task == "P"), 
                      aes(x = frequency_cds_scaled, y = accuracy_strict, color = group, fill = group)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
  scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
  labs(x= "Scaled CDS log-frequency") +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  theme_minimal() +
  theme(legend.position = "none")

(acc_PL_P_p1 | acc_PL_P_p2 | acc_PL_P_p3) + plot_annotation(title = "Polish Production") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

###  Comprehension RTs

```{r pl-rt-comp-plot}
rt_PL_C_p1 <- ggplot(data_pl_out_outliers %>% filter(task == "C"), 
                      aes(x = AoA, y = logRT, color = group, fill = group)) +
  geom_smooth(method = "lm", se = TRUE) +
  scale_y_continuous(
    name = "log Reaction Times",
    limits= c(7.5,8.5)) +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  labs(x = "AoA (in years)") +
  theme_minimal()

rt_PL_C_p2 <- ggplot(data_pl_out_outliers %>% filter(task == "C"), 
                     aes(x = Imageability, y = logRT, color = group, fill = group)) +
  geom_smooth(method = "lm", se = TRUE) +
  scale_y_continuous(
    name = "log RT",
    limits= c(7.5,8.5)) +
  scale_color_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  scale_fill_manual(
    name = "Group",
    values = c("monoPL" = "blue", "bi" = "red"),
    labels = c("Monolinguals", "Bilinguals")
  ) +
  labs(x = "Imageability (1 to 7)") +
  theme_minimal()
  theme(legend.position = "none")
  
rt_PL_C_p3 <- ggplot(data_pl_out_outliers %>% filter(task == "C"), 
                       aes(x = frequency_cds_scaled, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Scaled CDS log-frequency") +
    theme_minimal()
  theme(legend.position = "none")

(rt_PL_C_p1 | rt_PL_C_p2 | rt_PL_C_p3) + plot_annotation(title = "Polish Comprehension") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

###  Production RTs

```{r pl-rt-prod-plot}
rt_PL_P_p1 <- ggplot(data_pl_out_outliers %>% filter(task == "P"), 
                       aes(x = AoA, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "AoA (in years)") +
    theme_minimal()
  
  rt_PL_P_p2 <- ggplot(data_pl_out_outliers %>% filter(task == "P"), 
                       aes(x = Imageability, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Imageability (1 to 7)") +
    theme_minimal()
  theme(legend.position = "none")
  
  rt_PL_P_p3 <- ggplot(data_pl_out_outliers %>% filter(task == "P"), 
                       aes(x = frequency_cds_scaled, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoPL" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Scaled CDS log-frequency") +
    theme_minimal()
  theme(legend.position = "none")
  
  (rt_PL_P_p1 | rt_PL_P_p2 | rt_PL_P_p3) + plot_annotation(title = "Polish Production") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

##  Norwegian

### Comprehension Accuracy

```{r no-acc-comp-plot}
acc_NOR_C_p1 <- ggplot(data_no %>% filter(task == "C"), 
                        aes(x = AoA, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(
      name = "Accuracy (%)",
      limits = c(0, 1),
      labels = scales::percent_format(accuracy = 1)
    ) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "AoA (in years)") +
    theme_minimal()
  
  
acc_NOR_C_p2 <- ggplot(data_no %>% filter(task == "C"), 
                        aes(x = Imageability, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
    labs(x = "Imageability (0 to 7)") +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    theme_minimal()+
    theme(legend.position = "none")
  
  acc_NOR_C_p3 <- ggplot(data_no %>% filter(task == "C"), 
                        aes(x = frequency_cds_scaled, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
    labs(x= "Scaled CDS log-frequency") +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    theme_minimal() +
    theme(legend.position = "none")
  
(acc_NOR_C_p1 | acc_NOR_C_p2 | acc_NOR_C_p3) + plot_annotation(title = "Norwegian Comprehension") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

### Production Accuracy

```{r no-acc-prod-plot}
acc_NOR_P_p1 <- ggplot(data_no %>% filter(task == "P"), 
                         aes(x = AoA, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(
      name = "Accuracy (%)",
      limits = c(0, 1),
      labels = scales::percent_format(accuracy = 1)
    ) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "AoA (in years)") +
    theme_minimal()
  
  
acc_NOR_P_p2 <- ggplot(data_no %>% filter(task == "P"), 
                         aes(x = Imageability, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
    labs(x = "Imageability (0 to 7)") +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    theme_minimal()+
    theme(legend.position = "none")
  
acc_NOR_P_p3 <- ggplot(data_no %>% filter(task == "P"), 
                         aes(x = frequency_cds_scaled, y = accuracy_strict, color = group, fill = group)) +
    geom_smooth(method = "glm", method.args = list(family = "binomial"(link = "logit")), se = TRUE) +
    scale_y_continuous(name = "Accuracy (%)", limits = c(0, 1), labels = scales::percent_format(accuracy = 1)) +
    labs(x= "Scaled CDS log-frequency") +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    theme_minimal() +
    theme(legend.position = "none")
  
(acc_NOR_P_p1 | acc_NOR_P_p2 | acc_NOR_P_p3) + plot_annotation(title = "Norwegian Production") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
  

```

### Comprehension RTs

```{r no-rt-comp-plot}
rt_NOR_C_p1 <- ggplot(data_no_out_outliers %>% filter(task == "C"), 
                       aes(x = AoA, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "AoA (in years)") +
    theme_minimal()
  
rt_NOR_C_p2 <- ggplot(data_no_out_outliers %>% filter(task == "C"), 
                       aes(x = Imageability, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Imageability (1 to 7)") +
    theme_minimal()
  theme(legend.position = "none")
  
rt_NOR_C_p3 <- ggplot(data_no_out_outliers %>% filter(task == "C"), 
                       aes(x = frequency_cds_scaled, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Scaled CDS log-frequency") +
    theme_minimal()
  theme(legend.position = "none")
  
(rt_NOR_C_p1 | rt_NOR_C_p2 | rt_NOR_C_p3) + plot_annotation(title = "Norwegian Comprehension") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
  
```

### Production RTs

```{r no-rt-prod-plot}
rt_NOR_P_p1 <- ggplot(data_no_out_outliers %>% filter(task == "P"), 
                        aes(x = AoA, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "AoA (in years)") +
    theme_minimal()
  
rt_NOR_P_p2 <- ggplot(data_no_out_outliers %>% filter(task == "P"), 
                        aes(x = Imageability, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Imageability (1 to 7)") +
    theme_minimal()
  theme(legend.position = "none")
  
rt_NOR_P_p3 <- ggplot(data_no_out_outliers %>% filter(task == "P"), 
                        aes(x = frequency_cds_scaled, y = logRT, color = group, fill = group)) +
    geom_smooth(method = "lm", se = TRUE) +
    scale_y_continuous(
      name = "log RT",
      limits= c(7.5,8.5)) +
    scale_color_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    scale_fill_manual(
      name = "Group",
      values = c("monoNO" = "blue", "bi" = "red"),
      labels = c("Monolinguals", "Bilinguals")
    ) +
    labs(x = "Scaled CDS log-frequency") +
    theme_minimal()
  theme(legend.position = "none")
  
(rt_NOR_P_p1 | rt_NOR_P_p2 | rt_NOR_P_p3) + plot_annotation(title = "Norwegian Production") + plot_layout(guides = "collect") & theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
```

## Join plots

```{r join-plots}
  make_title_row <- function(label) {
    ggplot() +
      annotate("text", x = 0.5, y = 0.5, label = label,
               size = 5, fontface = "bold", hjust = 0.5) +
      theme_void()
  }
  
  row_titles <- c(
    "A. Polish Comprehension",
    "B. Polish Production",
    "C. Norwegian Comprehension",
    "D. Norwegian Production"
  )
  
  row_plots_accuracy <- list(
    acc_PL_C_p1 + acc_PL_C_p2 + acc_PL_C_p3,
    acc_PL_P_p1 + acc_PL_P_p2 + acc_PL_P_p3,
    acc_NOR_C_p1 + acc_NOR_C_p2 + acc_NOR_C_p3,
    acc_NOR_P_p1 + acc_NOR_P_p2 + acc_NOR_P_p3
  )
  
  row_plots_RT <- list(
    rt_PL_C_p1 + rt_PL_C_p2 + rt_PL_C_p3,
    rt_PL_P_p1 + rt_PL_P_p2 + rt_PL_P_p3,
    rt_NOR_C_p1 + rt_NOR_C_p2 + rt_NOR_C_p3,
    rt_NOR_P_p1 + rt_NOR_P_p2 + rt_NOR_P_p3
  )
  
  rows_accuracy <- list()
  for (i in seq_along(row_titles)) {
    title <- make_title_row(row_titles[i])
    plot_row <- row_plots_accuracy[[i]]
    rows_accuracy[[length(rows_accuracy) + 1]] <- title
    rows_accuracy[[length(rows_accuracy) + 1]] <- plot_row
  }
  
  rows_rt <- list()
  for (i in seq_along(row_titles)) {
    title <- make_title_row(row_titles[i])
    plot_row <- row_plots_RT[[i]]
    rows_rt[[length(rows_rt) + 1]] <- title
    rows_rt[[length(rows_rt) + 1]] <- plot_row
  }
  
  final_plot_accuracy <- wrap_plots(rows_accuracy, ncol = 1, heights = rep(c(0.18, 1), 4), guides = "collect") &
    theme(legend.position = "bottom")
  
  final_plot_rt <- wrap_plots(rows_rt, ncol = 1, heights = rep(c(0.18, 1), 4), guides = "collect") &
    theme(legend.position = "bottom")
  
  final_plot_accuracy
  final_plot_rt
  
ggsave("Accuracy Panel.png", plot = final_plot_accuracy, width = 12, height = 16, dpi = 300)
ggsave("RT Panel.png", plot = final_plot_rt, width = 12, height = 16, dpi = 300)

```

## Effect Size Plots

```{r}
#params_PL_C_acc <- model_parameters(models_acc$polish_c_acc)
#params_PL_P_acc <- model_parameters(models_acc$polish_p_acc)
#params_NOR_C_acc <- model_parameters(models_acc$norwegian_c_acc)
#params_NOR_P_acc <- model_parameters(models_acc$norwegian_p_acc)

new_order <- c("groupbi", "Age_scaled","AoA_scaled", "frequency_cds_scaled", "imageability_scaled",
               "groupbi:AoA_scaled", 
               "groupbi:frequency_cds_scaled",
               "groupbi:imageability_scaled",
               "imageability_scaled:frequency_cds_scaled")
labels_dict <- c("groupbi" = "Group (bilinguals)",
                 "Age_scaled" = "Child's Age",
                 "AoA_scaled" = "AoA",
                 "frequency_cds_scaled"= "CDS Frequency",
                 "imageability_scaled"  = "Imageability",
                 "groupbi:AoA_scaled" = "Group x AoA",
                 "groupbi:frequency_cds_scaled" = "Group x CDS Frequency",
                 "groupbi:imageability_scaled" = "Group x Imageability",
                 "imageability_scaled:frequency_cds_scaled" = "Group x Imageability x CDS Frequency")

plot_model_effects <- function(model, params, title, new_order = NULL, labels_dict = NULL, ylim=c(-2.6, 2.6)) {
  
  # Colors for significant effects
  effect_palette <- c(
    "groupbi" = "#8CCE7D",
    "Age_scaled" = "#00416D",
    "AoA_scaled" = "#50aac8",
    "frequency_cds_scaled" = "#e6942a",
    "imageability_scaled" = "#df454f"
  )
  
  # CI calculations
  if(!all(c("ci_lower","ci_upper") %in% colnames(params))){
    ci_df <- as.data.frame(confint.merMod(model, method = "Wald"))
    ci_df$var <- rownames(ci_df)
    colnames(ci_df) <- c("ci_lower","ci_upper","term")
    rownames(ci_df) <- NULL
    ci_df <- ci_df %>% filter(!is.na(ci_lower))
    params <- params %>%
      left_join(ci_df, by = c("Parameter" = "term")) %>%
      rename(Coefficient = Coefficient, Parameter = Parameter)
  }
  
  viz <- params %>%
    rename(term = Parameter, estimate = Coefficient) %>%
    filter(term != "(Intercept)")

  # If no explicit ordering was supplied, keep the terms' natural order.
  if(is.null(new_order)){
    new_order <- unique(as.character(viz$term))
  }

  viz <- viz %>%
    mutate(term = factor(term, levels = new_order)) %>%
    arrange(term) %>%
    filter(!is.na(term), !is.na(estimate)) %>%
    mutate(sig = ifelse(!is.na(ci_lower) & ci_lower * ci_upper > 0, TRUE, FALSE),
           base_effect = sapply(strsplit(as.character(term), ":"), `[`, 2),
           base_effect = ifelse(base_effect == "" | is.na(base_effect), as.character(term), base_effect),
           color_final = ifelse(sig, effect_palette[base_effect], "grey70"))
  
  
  plot <- viz %>%
    ggplot(aes(y = estimate, x = term, ymin = ci_lower, ymax = ci_upper, color = color_final)) +
    geom_hline(yintercept = 0, linetype = 2) +
    geom_errorbar(width = 0.3, linewidth = 1) +
    geom_point(size = 3) +
    coord_flip() +
    labs(y = "Coefficient Estimate", x = NULL, title = title) +
    theme_classic() +
    scale_x_discrete(labels = if(is.null(labels_dict)) ggplot2::waiver() else labels_dict, limits = rev) +
    scale_color_identity() +
    scale_y_continuous(limits = ylim) +
    theme(
      text = element_text(face="bold", size=16),
      plot.title = element_text(hjust = 0.5),
      panel.spacing = unit(2, "lines")
    )
  
  return(plot)
}


# List of models
model_list <- list(
  "PL_C_acc" = models_acc$polish_c_acc,
  "PL_P_acc" = models_acc$polish_p_acc,
  "NOR_C_acc" = models_acc$norwegian_c_acc,
  "NOR_P_acc" = models_acc$norwegian_p_acc,
  "PL_C_rt" = models_rt_simpler$polish_c_rt,
  "PL_P_rt" = models_rt_simpler$polish_p_rt,
  "NOR_C_rt" = models_rt_simpler$norwegian_c_rt,
  "NOR_P_rt" = models_rt_simpler$norwegian_p_rt
)

titles <- c(
  "Polish Comprehension",
  "Polish Production",
  "Norwegian Comprehension",
  "Norwegian Production",
  "Polish Comprehension",
  "Polish Production",
  "Norwegian Comprehension",
  "Norwegian Production"
)

# OX limits depending on models
lims <- ifelse(grepl("_acc", names(model_list)), list(c(-2.5, 2.5 )), list(c(-0.25, 0.25)))

plots_list <- list()

for(i in seq_along(model_list)){
  model <- model_list[[i]]
  name <- names(model_list)[i]
  
  if(grepl("_acc", name)){
    params <- model_parameters(model) %>% as.data.frame() %>% rename(Coefficient = Coefficient, Parameter = Parameter)
  } else {
    params <- as.data.frame(tidy(model))
    ci_df <- as.data.frame(confint.merMod(model, method = "Wald"))
    ci_df$var <- rownames(ci_df)
    colnames(ci_df) <- c("ci_lower","ci_upper","term")
    rownames(ci_df) <- NULL
    ci_df <- ci_df %>% filter(!is.na(ci_lower))
    params <- params %>%
      left_join(ci_df, by = c("term" = "term")) %>%
      rename(Coefficient = estimate, Parameter = term)
  }
  
  plot <- plot_model_effects(
    model = model,
    params = params,
    title = titles[i],
    new_order = new_order,
    labels_dict = labels_dict,
    ylim = lims[[i]]
  )
  
  plots_list[[name]] <- plot
}


row1 <- plots_list$PL_C_acc + plots_list$NOR_C_acc
row2 <- plots_list$PL_P_acc  + plots_list$NOR_P_acc
row3 <- plots_list$PL_C_rt + plots_list$NOR_C_rt
row4 <- plots_list$PL_P_rt + plots_list$NOR_P_rt

horizontal_line <- ggplot() +
  geom_hline(yintercept = 0.2, color = "black", linetype = "solid", linewidth = 0.5) +
  theme_void() +
  theme(plot.margin = margin(0, 0, 0, 0))

title_accuracy <- ggplot() +
  annotate("text", x = 0.5, y = 0.5, label = "A. Accuracy", size = 8, fontface = "bold", hjust = 0.5) +
  theme_void()

title_rt <- ggplot() +
  annotate("text", x = 0.5, y = 0.5, label = "B. Response times", size = 8, fontface = "bold", hjust = 0.5) +
  theme_void()


panel_effects_all <- title_accuracy / row1 / row2  / horizontal_line / title_rt / row3 / row4 +   plot_layout(heights = c(0.5, 3, 3, 0.3, 0.4, 3, 3))


panel_effects_all

ggsave("Effect sizes Panel.png", plot = panel_effects_all, width = 13, height = 16, dpi = 300)
```

