---
title: "BLC CLT and Word Properties"
date: "2026-04-01"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
options(scipen = 999) #removes scietific notation
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lme4)
library(broom.mixed) #for RMarkdown tables
library(knitr) #for RMarkdown tables
library(afex)
library(gtsummary)
library(flextable)
library(officer)
```

```{r data, include=FALSE}
data_pl <- read_csv("data_clt_wp_pl_anon.csv")
data_no <- read_csv("data_clt_wp_no_anon.csv")
```

## Data prepation

Step 1. Removing outliers from RTs
Outliers are defined as RTs that are both higher 
than mean RT + 3SD of a given child in a given task 
AND mean RT + 3SD of a given task

Database filtered for complete datapoints (frequency), 
correct responses and measured RTs higher than 1000 ms 
(lower are typically measurement errors)

Step 2. Scaling

```{r outliers-rts-pl, include=FALSE}
data_pl_filtered <- data_pl %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_pl_filtered$reaction_time) 
#there are 11236 measured reaction times for correct responses and complete cases, 
#RTs>=1000 ms

mean_RT_PL <- data_pl_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_PL <- mean_RT_PL %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_pl_with_outliers <- data_pl_filtered %>%
  left_join(mean_RT_PL, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_pl_meanRTs <- data_pl_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), 
            .groups = "drop")

data_pl_with_outliers <- data_pl_with_outliers %>%
  left_join(data_pl_meanRTs , by = "task") %>%
  mutate(outlier_overall = (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_PL <- data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_PL)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
#We also scale the frequency, imageability and AoA
#This database will be used for the analyses of the reaction times
data_pl_out_outliers <- data_pl_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")
```

```{r scale-pl, include=FALSE}
#data without RT outliers for RT analyses
#frequency is on a log scale but frquency cds needs to be transformed
data_pl_out_outliers <- data_pl_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds),
                                     center = T, scale = T),
    frequency_scaled = scale(FrequencyLemmaLog, 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time))

data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#data with RT outliers for accuracy analyses
data_pl <- data_pl %>%
  mutate(
     frequency_cds_scaled = scale(log(frequency_cds+1), 
                                      center = T, scale = T),
     frequency_scaled = scale(FrequencyLemmaLog, 
                              center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

summary(data_pl)
data_pl$group <-relevel(factor(data_pl$group), ref="monoPL")
```

```{r outliers-rts-no, include=FALSE}
data_no_filtered <- data_no %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_no_filtered$reaction_time)  
#there are 9850 measured reaction times for correct responses and complete cases, RTs>=1000 ms
  
mean_RT_NOR <- data_no_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_NOR <- mean_RT_NOR %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_no_with_outliers <- data_no_filtered %>%
  left_join(mean_RT_NOR, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = 
           (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_no_meanRTs <- data_no_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), .groups = "drop")

data_no_with_outliers <- data_no_with_outliers %>%
  left_join(data_no_meanRTs , by = "task") %>%
  mutate(outlier_overall = 
           (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_no <- data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_no)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
data_no_out_outliers <- data_no_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
```

NO CDS frequency is scaled on the formula:
ln(x+1) (bc there are same frequencies = 0)

```{r scale-no, include=FALSE}
data_no_out_outliers <- data_no_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE),
    logRT=log(reaction_time))

data_no_out_outliers$group <-relevel(factor(data_no_out_outliers$group), ref="monoNO")

#and for accuracy analyses we only need scaling the variables, no outliers
data_no <- data_no %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency + 1), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, center = TRUE, 
                                scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

data_no$group <-relevel(factor(data_no$group), ref="monoNO")
```

## Correlations between word properties

```{r include = FALSE}
df_num <- data_pl %>%
  distinct(word, frequency_cds_scaled, frequency_scaled, Imageability, AoA) %>%
  select(-word)

cor_mat_spearman <- cor(df_num,
                        method = "spearman",
                        use = "complete.obs")

library(Hmisc)
cor_res <- rcorr(as.matrix(df_num), type = "spearman")
# correlation matrix
cor_res$r
# p-values
cor_res$P
```

```{r echo = FALSE}
library(corrplot)
corrplot(cor_res$r,
         p.mat = cor_res$P,
         sig.level = 0.05,
         method = "circle",
         type = "upper",
         tl.col = "black",
         diag = FALSE,
         insig = "blank")
```

Lack of correlation between frequency is suprising...

```{r echo =FALSE}
df_num %>% 
  ggplot(aes(x = frequency_scaled, y = frequency_cds_scaled)) +
  geom_point(color = "lightpink", alpha = .8) +
  theme_classic() +
  labs(x = "SUBTLEX",
       y = "CDS")
```

## Accuracy Models

We run all models together (divided only into accuracy and RTs):

1) Bind Polish and Norwegian data (with outliers)
2) Run and view accuracy models
3) Summarise the results

### Scale age and bind data

```{r acc-data-scale-age}
#scale and center age
data_pl$Age_scaled <- scale(data_pl$Age, center = T, scale = T)
data_no$Age_scaled <- scale(data_no$Age, center = T, scale = T)
```

```{r bind data}
bind_rows(data_pl, data_no) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full
```

### Prepare models

```{r models-accuracy-all}
formula_glmer <- accuracy_strict ~ group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        Age_scaled * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        imageability_scaled * frequency_cds_scaled +
                        (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) +
  (1 | word)

ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_acc    = list(language = "POLISH",    task = "P"),
  polish_c_acc    = list(language = "POLISH",    task = "C"),
  norwegian_p_acc = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_acc = list(language = "NORWEGIAN", task = "C")
)

models_acc <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full, language == cond$language & task == cond$task)
  glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)
})

# models
summary(models_acc)
```

Check convergence:
No warnings.

```{r convergence-acc-checks}
lapply(models_acc, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_acc$polish_c_acc)

library(gtsummary)
library(flextable)
library(officer)

gt_table <- tbl_regression(models_acc$polish_c_acc)
gt_table
doc <- read_docx() %>%
  body_add_flextable(as_flex_table(gt_table))

print(doc, target = "glmer_summary.docx")
```

### Polish Production

```{r}
summary(models_acc$polish_p_acc)
```

### Norwegian Comprehension

```{r}
summary(models_acc$norwegian_c_acc)
```

### Norwegian Production

```{r}
summary(models_acc$norwegian_p_acc)
```

### Extract table

```{r tables-accuracy-models}
# Build a merged table
merged_table <- tbl_merge(
  tbls = lapply(models_acc, function(m) tbl_regression(m, exponentiate = TRUE)),
  tab_spanner = names(models_acc)   # uses list names as column headers
)

# Export
doc <- read_docx() |>
  body_add_flextable(as_flex_table(merged_table))

print(doc, target = "glmer_summary.docx")
```


##  RTs models

### Scale age and bind data

```{r rt-data-scale-age}
#scale and center age
data_pl_out_outliers$Age_scaled <- scale(data_pl_out_outliers$Age, center = T, scale = T)
data_no_out_outliers$Age_scaled <- scale(data_no_out_outliers$Age, center = T, scale = T)
```

```{r bind-rt-data}
bind_rows(data_pl_out_outliers, data_no_out_outliers) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full_out_outliers
```

### Prepare all models

First more complex with random slopes:

```{r models-rts-all}
formula_lmer <- logRT ~ group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        Age_scaled * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        imageability_scaled * frequency_cds_scaled +
                        (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + 
  (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt)
```

Most models did not converge: _boundary (singular) fit_

```{r convergence-rt-checks}
lapply(models_rt, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

We proceed with simpler models (no random slopes)

```{r models-rts-all-simple}
formula_lmer_simpler <- logRT ~ group * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        Age_scaled * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
                        imageability_scaled * frequency_cds_scaled +
                        (1 | child_id) + (1 | word)

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

#models
conditions <- list(
  polish_p_rt    = list(language = "POLISH",    task = "P"),
  polish_c_rt    = list(language = "POLISH",    task = "C"),
  norwegian_p_rt = list(language = "NORWEGIAN", task = "P"),
  norwegian_c_rt = list(language = "NORWEGIAN", task = "C")
)

models_rt_simpler <- lapply(conditions, function(cond) {
  df_sub <- subset(data_full_out_outliers, language == cond$language & task == cond$task)
  lmer(formula_lmer_simpler, data = df_sub, control = ctrl, REML = TRUE)
})

# models
summary(models_rt_simpler)
```

```{r convergence-rt-checks-2}
lapply(models_rt_simpler, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_rt_simpler$polish_c_rt)
```

### Polish Production

```{r}
summary(models_rt_simpler$polish_p_rt)
```

### Norwegian Comprehension

```{r}
summary(models_rt_simpler$norwegian_c_rt)
```

### Norwegian Production

```{r}
summary(models_rt_simpler$norwegian_p_rt)
```

### Export Tables

```{r}
# Build a merged table
merged_table_rt <- tbl_merge(
  tbls = lapply(models_rt_simpler, function(m) tbl_regression(m, exponentiate = TRUE)),
  tab_spanner = names(models_rt_simpler)   # uses list names as column headers
)

# Export
doc_rt <- read_docx() |>
  body_add_flextable(as_flex_table(merged_table_rt))

print(doc_rt, target = "lmer_summary.docx")
```
  

# Exposure and Accuracy

```{r select-bi}
data_full %>% filter(group == "bi") -> data_bi_full
```

```{r explore-exposure}
data_bi_full %>% 
  distinct(child_id, no_input_sum_percentage) %>%
  ggplot(aes(x = no_input_sum_percentage)) +
  geom_density()
  
data_bi_full %>% 
  distinct(child_id, pl_input_sum_percentage) %>%
  ggplot(aes(x = pl_input_sum_percentage)) +
  geom_density()
```

```{r exposure-accuracy-models}
conditions <- list(
  polish_p_exposure    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)

models_acc_exposure <- lapply(conditions, function(cond) {
  df_sub <- subset(data_bi_full, language == cond$language & task == cond$task)
  
  formula_glmer <- as.formula(paste0(
    "accuracy_strict ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + (1 | word)"
  ))
  
  glmer(formula_glmer, data = df_sub, control = ctrl, family = binomial)
})
```

```{r convergence-acc-exposure-checks}
lapply(models_acc_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_acc_exposure$polish_c_exposure)
```
 
### Polish Production

```{r}
summary(models_acc_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r}
summary(models_acc_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r}
summary(models_acc_exposure$norwegian_p_exposure)
``` 

# Exposure and RTs

```{r select-bi-no-outliers}
data_full_out_outliers %>% filter(group == "bi") -> data_bi_full_rt
```

```{r exposure-rt-models}
conditions <- list(
  polish_p_exposure_rt    = list(language = "POLISH",
                              task = "P",
                              input_var = "pl_input_sum_percentage"),
  polish_c_exposure_rt    = list(language = "POLISH",
                              task = "C",
                              input_var = "pl_input_sum_percentage"),
  norwegian_p_exposure_rt = list(language = "NORWEGIAN",
                              task = "P",
                              input_var = "no_input_sum_percentage"),
  norwegian_c_exposure_rt = list(language = "NORWEGIAN",
                              task = "C",
                              input_var = "no_input_sum_percentage")
)

models_rt_exposure <- lapply(conditions, function(cond) {
  df_sub <- subset(data_bi_full_rt, language == cond$language & task == cond$task)
  
  formula_lmer <- as.formula(paste0(
    "logRT ~ ", cond$input_var, " * (AoA_scaled + imageability_scaled + frequency_cds_scaled) +
     Age_scaled + imageability_scaled * frequency_cds_scaled +
     (1 | child_id) + (1 | word)"
  ))
  
  lmer(formula_lmer, data = df_sub, control = ctrl, REML = TRUE)
})
```

```{r convergence-rt-exposure-checks}
lapply(models_rt_exposure, function(m) {
  w <- m@optinfo$conv$lme4$messages
  if (is.null(w)) "OK" else w
})
```

### Polish Comprehension

```{r}
summary(models_rt_exposure$polish_c_exposure)
```
 
### Polish Production

```{r}
summary(models_rt_exposure$polish_p_exposure)
```
 
### Norwegian Comprehension

```{r}
summary(models_rt_exposure$norwegian_c_exposure)
``` 
 
### Norwegian Production

```{r}
summary(models_rt_exposure$norwegian_p_exposure)
``` 
  
