---
title: "BLC CLT and Word Properties"
date: "2026-04-01"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(lme4)
library(broom.mixed) #for RMarkdown tables
library(knitr) #for RMarkdown tables
library(afex)
```

```{r data, include=FALSE}
data_pl <- read_csv("data_clt_wp_pl_anon.csv")
data_no <- read_csv("data_clt_wp_no_anon.csv")
```

## Data prepation

Step 1. Removing outliers from RTs
Outliers are defined as RTs that are both higher 
than mean RT + 3SD of a given child in a given task 
AND mean RT + 3SD of a given task

Database filtered for complete datapoints (frequency), 
correct responses and measured RTs higher than 1000 ms 
(lower are typically measurement errors)

Step 2. Scaling

```{r outliers-rts-pl, include=FALSE}
data_pl_filtered <- data_pl %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_pl_filtered$reaction_time) 
#there are 11236 measured reaction times for correct responses and complete cases, RTs>=1000 ms

mean_RT_PL <- data_pl_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_PL <- mean_RT_PL %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_pl_with_outliers <- data_pl_filtered %>%
  left_join(mean_RT_PL, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_pl_meanRTs <- data_pl_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), 
            .groups = "drop")

data_pl_with_outliers <- data_pl_with_outliers %>%
  left_join(data_pl_meanRTs , by = "task") %>%
  mutate(outlier_overall = (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_PL <- data_pl_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_PL)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
#We also scale the frequency, imageability and AoA
#This database will be used for the analyses of the reaction times
data_pl_out_outliers <- data_pl_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")
```

```{r scale-pl, include=FALSE}
#data without RT outliers for RT analyses
#frequency is on a log scale but frquency cds needs to be transformed
data_pl_out_outliers <- data_pl_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds),
                                     center = T, scale = T),
    frequency_scaled = scale(FrequencyLemmaLog, 
                             center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = T, scale = T),
    AoA_scaled = scale(AoA, 
                       center = T, scale = T),
    logRT=log(reaction_time))

data_pl_out_outliers$group <-relevel(factor(data_pl_out_outliers$group), ref="monoPL")

#data with RT outliers for accuracy analyses
data_pl <- data_pl %>%
  mutate(
     frequency_cds_scaled = scale(log(frequency_cds+1), 
                                      center = T, scale = T),
     frequency_scaled = scale(FrequencyLemmaLog, 
                              center = T, scale = T),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

summary(data_pl)
data_pl$group <-relevel(factor(data_pl$group), ref="monoPL")
```

```{r outliers-rts-no, include=FALSE}
data_no_filtered <- data_no %>%
  filter(!is.na(reaction_time)) %>%
  filter(accuracy_strict == 1) %>%
  filter(reaction_time>=1000) %>%
  filter(complete.cases(frequency_cds, Imageability, AoA))
length(data_no_filtered$reaction_time)  
#there are 9850 measured reaction times for correct responses and complete cases, RTs>=1000 ms
  
mean_RT_NOR <- data_no_filtered %>%
  group_by(child_id, task) %>%
  summarise(mean_score = mean(reaction_time), 
            sd_score = sd(reaction_time), 
            .groups = "drop")

wide_df_RT_NOR <- mean_RT_NOR %>%
  pivot_wider(names_from = task, 
              values_from = c(mean_score, sd_score), 
              names_sep = "_")

data_no_with_outliers <- data_no_filtered %>%
  left_join(mean_RT_NOR, by = c("child_id", "task")) %>%
  mutate(outlier_per_child = 
           (reaction_time - mean_score) > 3 * sd_score)

#and now calculate the means for each task to find outliers
data_no_meanRTs <- data_no_with_outliers %>%
  group_by(task) %>%
  summarise(mean_absolut = mean(reaction_time),
            sd_absolut = sd(reaction_time), .groups = "drop")

data_no_with_outliers <- data_no_with_outliers %>%
  left_join(data_no_meanRTs , by = "task") %>%
  mutate(outlier_overall = 
           (reaction_time - mean_absolut) > 3 * sd_absolut)

outliers_only_no <- data_no_with_outliers %>%
  filter(outlier_per_child == TRUE & outlier_overall == TRUE)

summary(outliers_only_no)

#Now we exclude outliers from the database based on the two criteria (>M+3SD for child and for task)
data_no_out_outliers <- data_no_with_outliers %>%
  filter(!(outlier_per_child == TRUE & outlier_overall == TRUE))
```

NO CDS frequency is scaled on the formula:
ln(x+1) (bc there are same frequencies = 0)

```{r scale-no, include=FALSE}
data_no_out_outliers <- data_no_out_outliers %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, 
                                center = TRUE, scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE),
    logRT=log(reaction_time))

data_no_out_outliers$group <-relevel(factor(data_no_out_outliers$group), ref="monoNO")

#and for accuracy analyses we only need scaling the variables, no outliers
data_no <- data_no %>%
  mutate(
    frequency_cds_scaled = scale(log(frequency_cds+1),
                                 center = TRUE, scale = TRUE),
    frequency_scaled = scale(log(Frequency + 1), 
                             center = TRUE, scale = TRUE),
    imageability_scaled = scale(Imageability, center = TRUE, 
                                scale = TRUE),
    AoA_scaled = scale(AoA, 
                       center = TRUE, scale = TRUE))

data_no$group <-relevel(factor(data_no$group), ref="monoNO")
```

## Correlations between word properties

```{r include = FALSE}
df_num <- data_pl %>%
  distinct(word, frequency_cds_scaled, frequency_scaled, Imageability, AoA) %>%
  select(-word)

cor_mat_spearman <- cor(df_num,
                        method = "spearman",
                        use = "complete.obs")

library(Hmisc)
cor_res <- rcorr(as.matrix(df_num), type = "spearman")
# correlation matrix
cor_res$r
# p-values
cor_res$P
```

```{r echo = FALSE}
library(corrplot)
corrplot(cor_res$r,
         p.mat = cor_res$P,
         sig.level = 0.05,
         method = "circle",
         type = "upper",
         tl.col = "black",
         diag = FALSE,
         insig = "blank")
```

Lack of correlation between frequency is suprising...

```{r echo =FALSE}
df_num %>% 
  ggplot(aes(x = frequency_scaled, y = frequency_cds_scaled)) +
  geom_point(color = "lightpink", alpha = .8) +
  theme_classic() +
  labs(x = "SUBTLEX",
       y = "CDS")
```

##  Age effects

```{r}
#scale and center age
data_pl$Age_scaled <- scale(data_pl$Age, center = T, scale = T)
data_no$Age_scaled <- scale(data_no$Age, center = T, scale = T)
```

I will try to run all models together (divided only into accuracy and RTs):

1) Bind Polish and Norwegian data
2) Run and view accuracy models
3) Summarise the results

```{r bind data}
bind_rows(data_pl, data_no) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full
```

## Accuracy Models

```{r accuracy-models}
library(purrr)

# Define fixed parts once
rhs <- "~ group*(AoA_scaled + imageability_scaled + frequency_cds_scaled) +
          Age_scaled*(AoA_scaled + imageability_scaled + frequency_cds_scaled) +
          (1 + AoA_scaled + imageability_scaled + frequency_cds_scaled | child_id) + (1 | word) + imageability_scaled * frequency_cds_scaled"

ctrl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Define what varies
dvs   <- c("accuracy_strict")
tasks <- c("P", "C")
language <- c("POLISH", "NORWEGIAN")

# Create all combinations
combos <- expand.grid(dv = dvs, 
                      language = language, 
                      task = tasks, stringsAsFactors = FALSE)

# Fit all models
models <- pmap(combos, function(dv, language, task) {
  glmer(
    as.formula(paste(dv, rhs)),
    data    = data_full %>% filter(language == !!language) %>% filter(task == !!task),
    family  = binomial,
    control = ctrl
  )
})

# Name them clearly, e.g. "accuracy_strict.P", "accuracy_strict.C"
names(models) <- paste(combos$dv, combos$language, combos$task, sep = ".")
```

Check convergence:
No warnings.

```{r convergence-checks}
convergence_check <- map_dfr(models, function(m) {
  # Safely extract gradient
  derivs <- m@optinfo$derivs
  max_grad <- if (!is.null(derivs) && !is.null(derivs$gradient)) {
    max(abs(derivs$gradient))
  } else {
    NA_real_
  }
  
  # Safely extract warnings
  warns <- m@optinfo$conv$lme4$messages
  warn_str <- if (!is.null(warns)) paste(warns, collapse = "; ") else ""
  
  tibble(
    singular     = isSingular(m),
    warnings     = warn_str
  )
}, .id = "model")

convergence_check
```

### Polish Comprehension

```{r}
summary(models$accuracy_strict.POLISH.C)
```

### Polish Production

```{r}
summary(models$accuracy_strict.POLISH.P)
```


### Norwegian Comprehension

```{r}
summary(models$accuracy_strict.NORWEGIAN.C)
```

### Norwegian Production

```{r}
summary(models$accuracy_strict.NORWEGIAN.P)
```

##  RTs models

```{r}
#scale and center age
data_pl_out_outliers$Age_scaled <- scale(data_pl_out_outliers$Age, center = T, scale = T)
data_pl_out_outliers$Age_scaled <- scale(data_pl_out_outliers$Age, center = T, scale = T)
```

I will try to run all models together (divided only into accuracy and RTs):

1) Bind Polish and Norwegian data
2) Run and view accuracy models
3) Summarise the results

```{r bind data}
bind_rows(data_pl_out_outliers, data_no_out_outliers) %>%
  mutate(group = if_else(group == "bi","bi","mono")) %>%
  mutate(group = fct_relevel(group, "mono", "bi")) -> data_full_out_outliers
```

```{r}
library(purrr)

# Define fixed parts once
rhs <- "~ group*(AoA_scaled + imageability_scaled + frequency_cds_scaled) +
          Age_scaled*(AoA_scaled + imageability_scaled + frequency_cds_scaled) + 
(1 | child_id) + (1 | word) + imageability_scaled * frequency_cds_scaled"

ctrl <- lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))

# Define what varies
dvs   <- c("logRT")
tasks <- c("P", "C")
language <- c("POLISH", "NORWEGIAN")

# Create all combinations
combos <- expand.grid(dv = dvs, 
                      language = language, 
                      task = tasks, stringsAsFactors = FALSE)

# Fit all models
models <- pmap(combos, function(dv, language, task) {
  lmer(
    as.formula(paste(dv, rhs)),
    data    = data_full_out_outliers %>% 
      filter(language == !!language) %>% filter(task == !!task),
    control = ctrl
  )
})

# Name them clearly, e.g. "accuracy_strict.P", "accuracy_strict.C"
names(models) <- paste(combos$dv, combos$language, combos$task, sep = ".")
```

# Polish Comprehension

```{r}
summary(models_rt$logRT.POLISH.C)
```

# Polish Production

```{r}
summary(models_rt$logRT.POLISH.P)
```

# Norwegian Comprehension

```{r}
summary(models_rt$logRT.NORWEGIAN.C)
```

# Norwegian Production

```{r}
summary(models_rt$logRT.NORWEGIAN.P)
```

```{r}
data_full_out_outliers %>%
  filter(language == "NORWEGIAN", task == "P") %>%
  summarise(across(
    c(logRT, AoA_scaled, imageability_scaled,
      frequency_cds_scaled, Age_scaled),
    ~ sum(!is.na(.))
  ))
```

#RT models classic

PL COMP

```{r}
rt_pl_comp_age = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              Age_scaled*AoA_scaled + 
                              Age_scaled*imageability_scaled + 
                              Age_scaled*frequency_cds_scaled +
                              imageability_scaled*frequency_cds_scaled +
                              (1 | child_id) + (1 | word),
                          data = data_full_out_outliers %>% 
                            filter(task == "C") %>% filter(language == "POLISH"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5)))

summary(rt_pl_comp_age)
```

```{r}
rt_pl_prod_age = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              Age_scaled*AoA_scaled + 
                              Age_scaled*imageability_scaled + 
                              Age_scaled*frequency_cds_scaled +
                              imageability_scaled*frequency_cds_scaled +
                              (1 | child_id) + (1 | word),
                          data = data_full_out_outliers %>% 
                            filter(task == "P") %>% filter(language == "POLISH"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5)))

summary(rt_pl_prod_age)
```

#NO

```{r}
rt_no_comp_age = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              Age_scaled*AoA_scaled + 
                              Age_scaled*imageability_scaled + 
                              Age_scaled*frequency_cds_scaled +
                              imageability_scaled*frequency_cds_scaled +
                              (1 | child_id) + (1 | word),
                          data = data_full_out_outliers %>% 
                            filter(task == "C") %>% filter(language == "NORWEGIAN"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5)))

summary(rt_no_comp_age)
```

```{r}
rt_no__prod_age = lmer(logRT ~ group*AoA_scaled + 
                              group*imageability_scaled + 
                              group*frequency_cds_scaled +
                              Age_scaled*AoA_scaled + 
                              Age_scaled*imageability_scaled + 
                              Age_scaled*frequency_cds_scaled +
                              imageability_scaled*frequency_cds_scaled +
                              (1 | child_id) + (1 | word),
                          data = data_full_out_outliers %>% 
                            filter(task == "P") %>% filter(language == "NORWEGIAN"),
                          control = lmerControl(optimizer = "bobyqa", 
                                                optCtrl = list(maxfun = 2e5)))

summary(rt_no_prod_age)
```

# Exposure

```{r}
cor.test(data_no$Age, data_no$no_input_sum_percentage, method = "spearman")
data_no %>% ggplot(aes(x = no_input_sum_percentage, y = Age)) +
  geom_point()

data_pl %>% ggplot(aes(x = pl_input_sum_percentage, y = Age)) +
  geom_point()

cor.test(data_pl$Age, data_no$pl_input_sum_percentage, method = "spearman")
```

